\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper]{scrartcl}
\input{preamble/packages}
\input{preamble/redac}
\input{preamble/math_basics}
\input{preamble/math_mine}
\usepackage{csvsimple}

%I find these settings useful in draft mode. Should be removed for final versions.
	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
		\tolerance=2000
	%Accept overfull hbox up to...
		\hfuzz=2cm
	%Reduces verbosity about the bad line breaks.
		\hbadness 5000
	%Reduces verbosity about the underful vboxes.
		\vbadness=1300

\title{Compromise XPs}
\author[1]{Olivier Cailloux}
\author[2]{Ayça Ebru Giritligil}
\author[2]{Ipek Ozkal Sanver}
\author[1]{Remzi Sanver}
\affil[1]{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 PARIS, FRANCE}
\affil[2]{Bilgi, …}
\hypersetup{
	pdfsubject={Social choice},
	pdfkeywords={axiomatic analysis},
}

\begin{document}
\maketitle

%\begin{abstract}
%	
%\end{abstract}

\section{Introduction}
\label{sec:introduction}
Goal: investigate empirically the conditions in which people adopt a compromise notion based on minimal inequality of losses, as opposed to more classical compromise notions, in two-persons situations.

\section{Basic definitions and notation}
\label{sec:notation}
We have a non empty set of alternatives $\allalts$ with $\card{\allalts} = m$ and a set $N = \set{1, 2}$ of two individuals. 
Given $i \in N$, let $\ibar$ denote the other individual (and conversely, given $\ibar \in N$, let $i$ denote the other individual).
The possible profiles are $\linors^{\set{1, 2}}$. A \ac{SCR} is a function $f: \linors^{\set{1, 2}} → \powersetz{\allalts}$. 

Given $\prof = \set{(i, \prefi), (\ibar, \prefi[\ibar])} \in \allprofs$ and $x \in \allalts$, let $\lprof(x): N → \intvl{0, m - 1}$ associate to each individual $i \in N$ her loss at $x$, defined as the number of alternatives that are strictly preferred to $x$ in her preference $\prefi$, namely, $\lprof(x)_i = \card{\set{y \in \allalts \suchthat y \prefi x}}$, where $\set{y \in \allalts \suchthat y \prefi x}$ designate the upper contour set of $x$.
Let $\min\lprof(x) = \min_{i \in N}{\lprof(x)_i}$, $\max\lprof(x) = \max_{i \in N}{\lprof(x)_i}$ and $\sum \lprof(x) = \sum_{i \in N} \lprof(x)_i$ designate the minimal value, maximal value and sum of the losses of $x$.
Given a loss vector $l \in \alllosses$, define $d(l) = \abs{l_1 - l_2} = \max l - \min l$.

Given $\prof \in \allprofs$, the set of Pareto-optimal alternatives is 
$\POP
% = \set{x \in \allalts \suchthat \forall y \in \allalts \setminus \set{x}: x \prefi[1] y \lor x \prefi[2] y}
 = \set{x \in \allalts \suchthat \forall y \in \allalts, \exists i \in N \suchthat \lprof(x) ≤ \lprof(y)}$.
% = \set{x \in \allalts \suchthat \forall y \in \allalts, i \in N: \lprof(y)_i < \lprof(x)_i ⇒ \lprof(x)_{\ibar} < \lprof(y)_{\ibar}}$.

Note that $\argmin_{\POP} (d \circ \lprof) = \set{x \in \POP \suchthat (d \circ \lprof)(x) = \min_{y \in \POP} (d \circ \lprof)(y)}$ is the least unequal alternatives among the Pareto-optimal ones, according to the measure $d \circ \lprof$.
Also note that $\min_\allalts \max \lprof$ is the threshold that is reached when going from the first (best) rank downwards until some alternative is unanimously considered worth that rank or better. 

We study the “min spread” SCR $\MSP = \argmin_{\POP} (d \circ \lprof)$, which picks the least unequal alternatives among the Pareto-optimal ones, according to the differences of losses; the Fallback-Bargaining SCR \citep{Brams2001} $\FBP = \argmin_\allalts \max \lprof$; and the Borda SCR $B(P) = \argmin \sum \lprof$ which selects the alternatives that minimize the sum of losses.

\commentOC{We should have a look at \doi{10.1287/mnsc.2021.4025}.}

\section{Filtering and classifying profiles}
The results that this section refers to are proven in \cref{sec:proofs}.

\subsection{Filtering profiles}
We are interested in selecting profiles on which $\FB$ and $\MS$ disagree. 
As a minimal requirement, we thus request $\FBP \cap \MSP = \emptyset$. 
This implies $\card{\FBP} = 1$; $\card{\MSP} = 1$ (\cref{th:equiv}).

We also require $\prof$ to contain no Pareto-dominated alternative with a smaller spread than $\minineq[\POP]$.
This constraint stems from a desire to focus on the subject of our study, and not perturb the subject by letting alternatives that do not distinguish our rules of interest appear possibly attractive. Studying the attractivity of Pareto-dominated alternatives is an interesting goal but requires its own design.

Let $\fprofs = \set{\prof \in \allprofs \suchthat \FBP \cap \MSP = \emptyset \land \forall a \in \allalts: (d \circ \lprof)(a) ≥ \minineq[\POP]}$ designate the satisfactory profiles.

During a run with a given subject, we want the spread of the Fallback-Bargaining winner, $d(\lprof(x))$, to reach high enough values compared to $d(\lprof(y))$, in order to ensure a sufficient contrast with min spread, which requires a big enough value for $m$ as $\delta = d(\lprof(x)) - d(\lprof(y)) ≤ \floor{\frac{m - 1}{2}} - 2$ (\cref{th:delta}).
We also want $m$ to be small enough for cognitive simplicity. 
As a compromise, we opt for $m = 13$, which permits to reach $\delta = 4$.

\subsection{Classifying profiles}
\label{sec:classifying}
Given $\prof \in \fprofs$ (thus with $\card{\FBP} = \card{\MSP} = 1$), we write $\set{x} = \FBP$ and $\set{y} = \MSP$.

To each profile $\prof \in \fprofs$ can be associated these properties;:
\begin{enumerate}
	\item the losses of $x$ and $y$, $\lprof(x)$ and $\lprof(y)$;
	\item whether $x$ is also the Borda winner.
\end{enumerate}
Accordingly, we divide $\fprofs$ into classes of profiles and use a representative profile for each such class.

Let $T = \set{t \in \intvl{0, m - 1}^4 \suchthat t_1 < t_2 < t_3 < t_4 \land t_1 + t_4 + 1 ≤ t_2 + t_3 \land t_3 + t_4 ≤ m}$ denote the set of tuples of loss values that satisfy the specified constraints.
Given $t \in T$ and $i \in N$, define the class $C_{t, i} = \set{\prof \in \fprofs \suchthat \lprof(\FBP) = \set{(i, t_1), (\ibar, t_3)} \land \lprof(\MSP) = \set{(i, t_4), (\ibar, t_2)}}$ as the set of profiles where $\FBP$ and $\MSP$ have the specified losses (recall that $\FBP$ and $\MSP$ are singletons by definition of $\fprofs$ and using \cref{th:equiv}). 
Define the class $C_t = \bigcup_{i \in N} C_{t, i}$ as the set of profiles where $\FBP$ has the loss values $(t_1, t_3)$ and $\MSP$ has the loss values $(t_2, t_4)$ associated both with individuals $(i, \ibar)$ or both with $(\ibar, i)$. 
We consider the classes $\set{C_t, t \in T}$. 
This set of classes forms a complete cover of $\fprofs$ (\cref{th:cover}).

Within $\fprofs$, the Borda winner always differs from the Min spread winner (\cref{th:BMS}); and
here are the possible relationships between $B(\prof)$ and $\FBP$ (\cref{rk:BFB}):
\begin{itemize}
	\item if $t_1 = \min \lprof(x) = 0$, no profile from $\fprofs$ distinguish the Borda winner and the FB winner, formally, $\forall t \in T, \prof \in C_t: t_1 = 0 ⇒ B(\prof) = \FBP$;
	\item if $t_1 = \min \lprof(x) = 1$, $x \in B(\prof)$, with both $\FBP = B(\prof)$ and $\FBP \subset B(\prof)$ possible;
	\item if $t_1 = \min \lprof(x) ≥ 2$, both $\FBP = B(\prof)$ and $\FBP \cap B(\prof) = \emptyset$ are possible.
\end{itemize}

\subsection{Enumerating classes}
TODO obtain these bounds in general.
\begin{corollary}
	$\forall \prof \in \allprofs \suchthat \argmin_{\POP} (d \circ \lprof) \nsubseteq \FBP$, with $m = 13$:
	\begin{enumerate}
		\item $4 ≤ \max \lprof(y) ≤ 8$;
		\item $\max \set{2, 2 \max \lprof(y) - 12} ≤ \min \lprof(y) ≤ \min \set{12 - \max \lprof(y), \max \lprof(y) - 2}$;
		\item $\max \set{\min \lprof(y) + 1, \max \lprof(y) - \min \lprof(y) + 1} ≤ \max \lprof(x) ≤ \min \set{\max \lprof(y) - 1, 13 - \max \lprof(y)}$;
		\item $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y) + 1)$.
	\end{enumerate}
\end{corollary}

\begin{corollary}
	$\forall \prof \in \allprofs \suchthat \argmin_{\POP} (d \circ \lprof) \nsubseteq \FBP \land \max \lprof(y) ≤ 7$, with $m = 13$:
	\begin{enumerate}
		\item $4 ≤ \max \lprof(y) ≤ 7$;
		\item $2 ≤ \min \lprof(y) ≤ \max \lprof(y) - 2$;
		\item $\max \set{\min \lprof(y) + 1, \max \lprof(y) - \min \lprof(y) + 1} ≤ \max \lprof(x) ≤ \max \lprof(y) - 1$;%
		\footnote{The bound that triggers in $\max \set{\min \lprof(y) + 1, \max \lprof(y) - \min \lprof(y) + 1}$ depends whether $\min \lprof(y) ≥ \frac{\max \lprof(y)}{2}$;  which varies for all $5 ≤ \max \lprof(y) ≤ 7$ (they are equal for $\max \lprof(y) = 4$).}
		\item $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y) + 1)$.
	\end{enumerate}
\end{corollary}

\subsection{For m 13}
For $\max \lprof(y) = 8$, we get $4 ≤ \min \lprof(y) ≤ 4$.
For $\max \lprof(y) = 8$ and $\min \lprof(y) = 4$, we get $5 ≤ \max \lprof(x) ≤ 5$ and $\min \lprof(x) ≤ \max \lprof(x) - 5$ thus only $\max \lprof(x) = 5$ and $\min \lprof(x) = 0$ is possible.
For $\max \lprof(y) = 8$: 1 class.

For $\max \lprof(y) = 7$, we get $2 ≤ \min \lprof(y) ≤ 5$.
For $\max \lprof(y) = 7$ and $\min \lprof(y) = 5$, we get $6 ≤ \max \lprof(x) ≤ 6$ and $\min \lprof(x) ≤ \max \lprof(x) - 3$ thus only $\max \lprof(x) = 6$ and $0 ≤ \min \lprof(x) ≤ 3$ are possible.
For $\max \lprof(y) = 7$ and $\min \lprof(y) = 4$, we get $5 ≤ \max \lprof(x) ≤ 6$ and $\min \lprof(x) ≤ \max \lprof(x) - 4$ thus only $\max \lprof(x) = 6$ and $0 ≤ \min \lprof(x) ≤ 2$; and $\max \lprof(x) = 5$ and $0 ≤ \min \lprof(x) = 1$ are possible.
For $\max \lprof(y) = 7$ and $\min \lprof(y) = 3$, we get $5 ≤ \max \lprof(x) ≤ 6$ and $\min \lprof(x) ≤ \max \lprof(x) - 5$ thus only $\max \lprof(x) = 6$ and $0 ≤ \min \lprof(x) ≤ 1$; and $\max \lprof(x) = 5$ and $\min \lprof(x) = 0$ are possible.
For $\max \lprof(y) = 7$ and $\min \lprof(y) = 2$, we get $6 ≤ \max \lprof(x) ≤ 6$ and $\min \lprof(x) ≤ \max \lprof(x) - 6$ thus only $\max \lprof(x) = 6$ and $\min \lprof(x) = 0$ is possible.
For $\max \lprof(y) = 7$: 13 classes.

For $\max \lprof(y) = 6$, we get $2 ≤ \min \lprof(y) ≤ 4$.
For $\max \lprof(y) = 6$ and $\min \lprof(y) = 4$, we get $5 ≤ \max \lprof(x) ≤ 5$ and $\min \lprof(x) ≤ \max \lprof(x) - 3$ thus only $\max \lprof(x) = 5$ and $0 ≤ \min \lprof(x) ≤ 2$ are possible.
For $\max \lprof(y) = 6$ and $\min \lprof(y) = 3$, we get $4 ≤ \max \lprof(x) ≤ 5$ and $\min \lprof(x) ≤ \max \lprof(x) - 4$ thus only $\max \lprof(x) = 5$ and $0 ≤ \min \lprof(x) ≤ 1$; and $\max \lprof(x) = 4$ and $\min \lprof(x) = 0$ are possible.
For $\max \lprof(y) = 6$ and $\min \lprof(y) = 2$, we get $5 ≤ \max \lprof(x) ≤ 5$ and $\min \lprof(x) ≤ \max \lprof(x) - 5$ thus only $\max \lprof(x) = 5$ and $\min \lprof(x) = 0$ is possible.
For $\max \lprof(y) = 6$: 7 classes.

For $\max \lprof(y) = 5$, we get $2 ≤ \min \lprof(y) ≤ 3$.
For $\max \lprof(y) = 5$ and $\min \lprof(y) = 3$, we get $4 ≤ \max \lprof(x) ≤ 4$ and $\min \lprof(x) ≤ \max \lprof(x) - 3$ thus only $\max \lprof(x) = 4$ and $0 ≤ \min \lprof(x) ≤ 1$ are possible.
For $\max \lprof(y) = 5$ and $\min \lprof(y) = 2$, we get $4 ≤ \max \lprof(x) ≤ 4$ and $\min \lprof(x) ≤ \max \lprof(x) - 4$ thus only $\max \lprof(x) = 4$ and $\min \lprof(x) = 0$ is possible.
For $\max \lprof(y) = 5$: 3 classes.

For $\max \lprof(y) = 4$, we get $2 ≤ \min \lprof(y) ≤ 2$.
For $\max \lprof(y) = 4$ and $\min \lprof(y) = 2$, we get $3 ≤ \max \lprof(x) ≤ 3$ and $\min \lprof(x) ≤ \max \lprof(x) - 3$ thus only $\max \lprof(x) = 3$ and $\min \lprof(x) = 0$ is possible.
For $\max \lprof(y) = 4$: 1 class.

\begin{table}
	\begin{tabular}{CCCllCCCCCC}
		\toprule
		\text{id} & \scriptscriptstyle d(\lprof(x)) & \scriptscriptstyle d(\lprof(y)) & v(x) & v(y) & e & \scriptscriptstyle \text{top} & \scriptscriptstyle \Delta^\text{min} & \scriptscriptstyle \Delta^\text{avg} & \scriptscriptstyle \Delta^\text{ineq}&\text{cl}\\
		\midrule 
		\csvreader[late after line = \\]{Profiles.csv}%
		{dlPx = \dlpx, dlPy = \dlpy, max lPx = \maxlpx, max lPy = \maxlpy, min lPx = \minlpx, avg lPx = \avglPx, min lPy = \minlpy, avg lPy = \avglpy, e = \cole, top = \coltop, dmin = \dmin, davg = \davg, delta = \coldelta, cl coarse = \clcoarse, subclass = \subclass}{%
			\thecsvrow & \dlpx & \dlpy & (\minlpx, \maxlpx, \num[round-precision = 1]{\avglPx}) & (\minlpy, \maxlpy, \avglpy) & \cole & \coltop & \dmin & \davg & \coldelta & \clcoarse.\subclass
		}% 
		\bottomrule
	\end{tabular}
	\caption{Possible values for $m = 13$; $v(z) = (\min \lprof(z), \max \lprof(z), \frac{\sum \lprof(z)}{2})$; top indicates whether $\min \lprof(x) = 0$; $\Delta^\text{ineq} = d(\lprof(x)) - d(\lprof(y))$}
	\label{fig:m13}
\end{table}

\Cref{fig:m13} lists the coherent values for these variables. 
To identify narrow classes (rows in the table), consider $\Delta^\text{min}$ or $\Delta^\text{avg}$, $\delta$, $\min \lprof(x)$, $\max \lprof(x)$.
To identify wide classes (indicated in “cl”), consider top, $\Delta^\text{min}$ or $\Delta^\text{avg}$, and $\Delta^\text{ineq}$.

\subsection{Some profile classes (automatic)}
\input{examples.tex}

\subsection{Some profile classes (manual)}
\begin{example}[$\Delta^\text{min} = 2$; $\delta = 1$; $\lprof(x) = (0, 6)$ thus cl $1$]
	\label{ex1.1}
	\begin{equation}
		\begin{array}{*{13}l}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & h & & & & \bm{a}
		\end{array} 
	\end{equation}
\end{example}

\begin{example}[$\Delta^\text{min} = 2$; $\delta = 1$; $\lprof(x) = (0, 3)$ thus cl $1$]
	\label{ex:06}
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & e & \bm{a}
		\end{array}
	\end{equation}
\end{example}

\begin{example}[$\Delta^\text{min} = 2$; $\delta = 1$; $\lprof(x) = (1, 6)$ thus cl $11$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& \bm{b}	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & h & & & \bm{b}
		\end{array}
	\end{equation}
\end{example}

\begin{example}[$\Delta^\text{min} = 2$; $\delta = 1$; $\lprof(x) = (3, 6)$ thus cl $11$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& b	& c	& \bm{d}	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{d}
		\end{array}
	\end{equation}
\end{example}

\begin{example}[spread $x$: 6, spread $y$: 3, $\max \lprof(y) = 7$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & h & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}[spread $x$: 6, spread $y$: 3, $\max \lprof(y) = 8$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & i & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}[spread $x$: 4, spread $y$: 2, $\rho = 6$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& b	& \bm{c}	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{c}
		\end{array}
	\end{equation}
\end{example}

\begin{example}[spread $x$: 4, spread $y$: 2, $\rho = 4$]
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & f & \bm{a} & & & & & l & m & j & k
		\end{array}
	\end{equation}
	The end is set to ease choice.
\end{example}

\begin{example}[spread $x$: 6, spread $y$: 2]
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$, with $g$ not just after $a$.
\end{example}

\subsection{Classes}
Given a profile $P$ with a single FB winner and a single MS winner, let $\set{x} = FB(\prof)$ and $\set{y} = MS(\prof)$ denote the corresponding alternatives. One can associate to such a profile $\prof$ the four numbers $(\min \lprof(x), \max \lprof(x), \min \lprof(y), \max \lprof(y))$.
This determines the losses of the FB and the MS winner.
Assume that $\max \lprof(x) ≤ 9$ and $\max \lprof(y) ≤ 9$. In such a case, the tuple can be given simply as a four digits number, such as 0324 for $(\min \lprof(x) = 0, \max \lprof(x) = 3, \min \lprof(y) = 2, \max \lprof(y) = 4)$. 
Furthermore, once the losses of the FB and the MS winner are specified, there exists some systematic way of completing the profile to “ease choice” (described later), up to renaming the alternatives and voters. As a consequence, 

\section{Protocol}
\subsection{Questions}
Ceteris Paribus…
\begin{enumerate}
	\item Does high $\Delta$ favor MS?
	\begin{itemize}
%		\item $\delta = 4 ⇔ \Delta^\text{min} = 5$ and  $\delta = 4 ⇒ \Delta^\text{avg} = 3$.
		\item {}[0324 (15) or 0526 (20)] VS 0657 (1)
		\item or any other $\Delta^\text{ineq} = 1$ VS 0657
%		\item $\delta = 3 ⇔ 
	\end{itemize}
	\item Does it matter for the FB winner to be top-ranked by a voter? 
	\begin{itemize}
		\item 0324 (15) VS 1435 (14)
		\item 0526 (20) VS 1637 (19, not taken)
	\end{itemize}
	\item Does the best position of the FB winner matter?
	\begin{itemize}
		\item 0324 (15) VS 3657 (12)
	\end{itemize}
	\item Does $d(\lprof(y))$ matter, fixing $\Delta^\text{ineq}$?
	\begin{itemize}
		\item{} [0546 (3) or 1657 (2)] VS 0647 (4)
	\end{itemize}
	\item Does showing profiles in favor of MS first favor MS choices in other profiles?
	\item Does using the word “compromise” matter or using scenario  versus abstract presentation?
	\item Does $FB(P) = B(P)$ increase the propension to select the $FB$ winner?
	\item Do people select Borda rather than FB or MS?
\end{enumerate}
As a consequence, we pick the following set of seven profiles: $\set{0324 (15), 0526 (20), 0657 (1), \allowbreak 1435 (14), \allowbreak 3657 (12), \allowbreak 0546 (3), 0647 (4)}$.
Note that 3657 (12) has $B ≠ FB$ so it might point out a disagreement with our notion of compromise.
\commentOC{Is it possible to first check that subjects indeed generally pick one of our expected alternatives (i.e., the FB or MS winner), and ask subjects for a reason when their choice differs from this expectation?}

\subsection{Protocol}
We could run an abstract setting. We use the word compromise. (If we have enough money we can also investigate the abstract-non-compromise wording, though Olivier is a bit skeptical about the interest of this version.)
We also might compare two or three scenarios, one of which that describes a situation where envy matters, but we might still have to convince Ayça about this.
We do not pinpoint $x$ or $y$: subjects can choose any alternative.

Towards the end of the sequence, we use a seventh prime profile, to check for consistency.

We use two sequences. $S_1$ orders profiles from the most to the least MS-favoring profiles, and $S_2$ is $S_1$ reversed. How much a profile is MS-favoring is determined using these criteria, lexicographically.
\begin{itemize}
	\item high $\Delta^\text{ineq}$
	\item small $\Delta^\text{avg}$
	\item small $d(\lprof(y))$
	\item high $\min \lprof(x)$
\end{itemize}

We pick a random permutation to rename alternatives, for each choice we present.

We ask for how they choose, their rationale, for each choice we present. Subjects answer using free text and must provide some text before continuing.

\subsection{An example run}
\input{run.tex}

\bibliography{biblio}

\appendix
\section{Formal statements}
\label{sec:proofs}

\subsection{General results}
\begin{theorem}
	\label{th:maxFB}
	$\forall \prof \in \allprofs: \min \max \lprof ≤ \khalf$.
\end{theorem}
\begin{proof}
	Define $A = \set{a \in \allalts \suchthat 0 ≤ \lprof(a)_1 ≤ \khalf}$.
	Define $B = \set{a \in \allalts \suchthat \khalf < \lprof(a)_2 ≤ m - 1}$.
	Observe that $\card{A} = \khalf + 1$ and $\card{B} = (m - 1) - \khalf = (m - \khalf) - 1 = \ceil{\frac{m}{2}} - 1 ≤ \khalf$, thus, $\card{B} < \card{A}$.
	Thus, $\exists x \in A \setminus B$.
	Thus, $\lprof(x)_1 ≤ \khalf$ (as $x \in A$) and $\lprof(x)_2 ≤ \khalf$ (as $x \notin B$).
	It follows that $\max \lprof(x) ≤ \khalf$.
\end{proof}

\begin{theorem}
	\label{th:FBPO}
	$\forall \prof \in \allprofs: \argmin \max \lprof \subseteq \POP$.
\end{theorem}
\begin{proof}
	Consider any $x \in \argmin \max \lprof$ and any $y \in \allalts$.
	
	Observe that $\max \lprof(x) ≤ \max \lprof(y)$, equivalently, $\forall i \in N: \lprof(x)_i ≤ \max y$.
	Thus, given any $i \in \argmax \lprof(y)$, $\lprof(x)_i ≤ \lprof(y)_i$.
\end{proof}

\subsection{Restraining profiles}
\begin{theorem}
	\label{th:equiv}
	The following propositions are equivalent:
	\begin{enumerate}
		\item \label{it:noInters} $\FBP \cap \MSP = \emptyset$;
		\item \label{it:order} $\forall y \in \MSP, x \in \FBP, i \in \argmax \lprof(y): \min \lprof(x) = \lprof(x)_i < \min \lprof(y) = \lprof(y)_{\ibar} < \max \lprof(x) = \lprof(x)_{\ibar} < \max \lprof(y) = \lprof(y)_i$.
	\end{enumerate}
	Furthermore, they imply:
	\begin{enumerate}[label=({\roman*}), ref={\roman*}]
		\item \label{it:singFBP} $\card{\FBP} = 1$;
		\item \label{it:singMSP} $\card{\MSP = 1}$;
		\item \label{it:ourMax} $\min \max \lprof ≤ \floor{\frac{m - 1}{2}}$.
	\end{enumerate}
\end{theorem}
\begin{proof}
	Assuming \cref{it:noInters}, let us prove \cref{it:order}.
	Pick any $x \in \FBP = \argmin \max \lprof$ and any $y \in \MSP = \argmin_{\POP} (d \circ \lprof)$.
	Thanks to \cref{it:noInters}, we know that $y \notin \FBP$ thus $\max \lprof(x) < \max \lprof(y)$;
	also, $x \in \POP$ (as given by \cref{th:FBPO}), thus $d(\lprof(y)) ≤ d(\lprof(x))$.
	
	We see that $\min \lprof(x) < \min \lprof(y)$ as otherwise $\min \lprof(y) ≤ \min \lprof(x) ≤ \max \lprof(x) < \max \lprof(y)$ which yields $d(\lprof(x)) < d(\lprof(y))$.
	
	Pick any $i \in \argmax \lprof(y)$.
	We can see that $\min \lprof(y) = \lprof(y)_{\ibar} < \lprof(x)_{\ibar}$. That is because $\max \lprof(x) < \max \lprof(y) = \lprof(y)_i$ thus $\lprof(x)_i ≤ \max \lprof(x) < \lprof(y)_i$ and as $y \in \POP$, we need to have $\lprof(y)_{\ibar} < \lprof(x)_{\ibar}$.

	So far we know that $\min \lprof(x) < \lprof(y)_{\ibar} < \lprof(x)_{\ibar}$ and $\max \lprof(x) < \lprof(y)_i$, which also permit to deduce that $\lprof(x)_i = \min \lprof(x)$ and $\lprof(x)_{\ibar} = \max \lprof(x)$.
	This establishes \cref{it:order}.
	
	In turn, \cref{it:order} implies \cref{it:noInters} as, picking any $y \in \MSP$, we see that $y \in \FBP$ is excluded by picking any $x \in \FBP$ and using $\max \lprof(x) < \max \lprof(y)$.
	
	We now turn to the consequences of these claims.
	Pick any $x \in \FBP$ and $y \in \MSP$ and $i \in \argmax \lprof(y)$. Thus, from \cref{it:order}, $\max \lprof(x) = \lprof(x)_{\ibar}$.
	
	Considering any $x' \in \FBP$, from \cref{it:order} again, $\max \lprof(x') = \lprof(x')_{\ibar}$. As $x, x' \in \FBP$, we also have $\max \lprof(x) = \max \lprof(x')$. Thus, $\lprof(x')_{\ibar} = \lprof(x)_{\ibar}$ and $x = x'$.
	
	A similar argument establishes \cref{it:singMSP}.
	
	Define $A = \set{a \in \allalts \suchthat \max \lprof(x) < \lprof(a)_i ≤ m - 1}$,
	$B = \set{a \in \allalts \suchthat 0 ≤ \lprof(a)_{\ibar} < \max \lprof(x)}$.
	As $\card{\FBP} = 1$ and $x \notin B$, $a \in B ⇒ a \notin \FBP$, whence $a \in B ⇒ \max \lprof(x) < \max \lprof(a) ⇒ \max \lprof(x) < \lprof(a)_i$ (because $a \in B ⇒ \lprof(a)_{\ibar} < \max \lprof(x)$), thus $B \subseteq A$.
	It follows that $\max \lprof(x) = \card{B} ≤ \card{A} = m - 1 - \max \lprof(x)$, whence $\max \lprof(x) ≤ \frac{m - 1}{2}$.
\end{proof}

From now on, each time we deal with profiles such that \cref{th:equiv} \cref{it:noInters} or \ref{it:order} holds, we will therefore consider, without explicitly invoking \cref{th:equiv}, that $\card{\FBP} = \card{\MSP} = 1$, thus, we will consider these sets as singletons, and similarly for the sets $\argmin \lprof(\FBP)$, $\argmax \lprof(\FBP)$, $\argmin \lprof(\MSP)$ and $\argmax \lprof(\MSP)$.

\subsection{Bounds on losses}
\begin{theorem}
	\label{th:sufficientBounds}
	$\forall \prof \in \allprofs \suchthat \FBP \cap \MSP = \emptyset$, letting $\set{x} = \FBP$, $\set{y} = \MSP$ and $\set{i} = \argmax \lprof(y)$, and defining $t_1 = \min \lprof(x)$, $t_2 = \min \lprof(y)$, $t_3 = \max \lprof(x)$ and $t_4 = \max \lprof(y)$:
	\begin{enumerate}
		\item \label{it:suffOrder} $t_1 = \lprof(x)_i < t_2 = \lprof(y)_{\ibar} < t_3 = \lprof(x)_{\ibar} < t_4 = \lprof(y)_i$;
		\item \label{it:suff1423} $t_1 + t_4 + 1 ≤ t_2 + t_3$;
		\item \label{it:suff34m} $t_3 + t_4 ≤ m$.
	\end{enumerate}
\end{theorem}
\begin{proof}
	\Cref{it:suffOrder} comes directly from \cref{th:equiv} \cref{it:order}.
	
	\Cref{it:suff1423} holds as $d(\lprof(y)) < d(\lprof(x))$, equivalently, $\max \lprof(y) - \min \lprof(y) < \max \lprof(x) - \min \lprof(x)$, thus, $t_4 - t_2 < t_3 - t_1$.
	
	To prove \cref{it:suff34m}, define $A = \set{a \in \allalts \suchthat 0 ≤ \lprof(a)_i < t_4}$ and $B = \set{a \in \allalts \suchthat t_3 ≤ \lprof(a)_{\ibar} ≤ m - 1}$.
	Pick $a \in A$. 
	As $\lprof(a)_i < t_4 = \lprof(y)_i$, $a ≠ y$. 
	As $y \in \POP$, $\lprof(y)_i < \lprof(a)_i \lor \lprof(y)_{\ibar} < \lprof(a)_{\ibar}$, thus $t_2 = \lprof(y)_{\ibar} < \lprof(a)_{\ibar}$.

	Now assume that $a \in A \cup \POP$. 
	As $t_3 = \max \lprof(x) = \min \max \lprof$, $t_3 ≤ \max \lprof(a)$. 
	Thus, if $\lprof(a)_i < t_3$ then $t_3 ≤ \lprof(a)_{\ibar}$.
	Otherwise, $t_3 ≤ \lprof(a)_i$, which also leads to $t_3 ≤ \lprof(a)_{\ibar}$ because otherwise $t_2 < t_3 ≤ \lprof(a)_i < t_4$ (as $a \in A$) and $t_2 < \lprof(a)_{\ibar} < t_3 < t_4$, implying $d(\lprof(a)) < t_4 - t_2 = d(\lprof(y))$, contradicting $y \in \MSP$.
	We conclude that $a \in A \cup \POP ⇒ t_3 ≤ \lprof(a)_{\ibar}$.
	
	Consider now $a \in A$, $a \notin \POP$.
	Thus $\exists a' \in \POP \suchthat \lprof(a')_i < \lprof(a)_i \land \lprof(a')_{\ibar} < \lprof(a)_{\ibar}$. Thus, $\lprof(a')_i < \lprof(a)_i < t_4$, whence $a' \in A$, which implies $t_3 ≤ \lprof(a')_{\ibar}$ and thus, again, $t_3 ≤ \lprof(a)_{\ibar}$.

	We obtain that $A \subseteq B$.
	But $\card{A} = t_4$ and $\card{B} = m - t_3$, thus establishing \cref{it:suff34m}.
\end{proof}

\commentOC{Idea. Define $T$ here. Here we know that any $P$ satisfies this $t$. Obtain consequent bounds on $t$ (as done in the proof of \cref{th:B}). Also, obtain equivalent bounds on $t$. Obtain \cref{th:delta} for free.}
Let $T = \set{t \in \intvl{0, m - 1}^4 \suchthat t_1 < t_2 < t_3 < t_4 \land t_1 + t_4 + 1 ≤ t_2 + t_3 \land t_3 + t_4 ≤ m}$ be defined as in \cref{sec:classifying}.
We start by listing some inequalities that $t$ satisfy that will reveal useful.
\begin{theorem}
	\label{th:consequentBounds}
	$\forall t \in T$:
	\begin{enumerate}
		\item \label{it:torder} $0 ≤ t_1 < t_2 < t_3 < t_4$ (thus $t_1 ≤ t_2 - 1$, $t_2 ≤ t_3 - 1$, $t_3 ≤ t_4 - 1$);
		\item \label{it:t1423} $t_1 + t_4 + 1 ≤ t_2 + t_3$;
		\item \label{it:t34m} $t_3 + t_4 ≤ m$;
		\item \label{it:t12} $t_1 ≤ t_2 - 2$;
		\item \label{it:t1m42} $t_1 ≤ m - 2 t_4 + t_2 - 1$;
		\item \label{it:t4231} $t_4 - t_2 ≤ t_3 - t_1 - 1$;
		\item \label{it:t13m} $t_1 + t_3 ≤ m - 4$.
	\end{enumerate}
\end{theorem}
\begin{proof}
	Let $t \in T$.
	\begin{itemize}
		\item \Cref{it:torder,it:t1423,it:t34m} hold by definition of $T$.
%		\item From \cref{it:t1423}, $t_1 - t_2 + 2 ≤ t_3 - t_4 + 1$ and from \cref{it:torder}, $t_3 - t_4 + 1 ≤ 0$, thus $t_1 - t_2 + 2 ≤ 0$, equivalently, \cref{it:t12}.
		\item \Cref{it:t1423} is equivalent to $0 ≤ t_2 - t_1 - 2 - (t_4 - t_3 - 1)$ and from \cref{it:torder}, $0 ≤ t_4 - t_3 - 1$, thus $0 ≤ t_2 - t_1 - 2$, equivalently, \cref{it:t12}.
		\item Using $t_3 ≤ m - t_4$ (from \cref{it:t34m}), together with \cref{it:t1423}, yields $t_1 ≤ - t_4 - 1 + t_2 + m - t_4$, equivalently, \cref{it:t1m42}.
		\item \Cref{it:t4231} rearranges \cref{it:t1423}.
		\item Finally, $t_1 ≤ t_2 - 2 ≤ t_3 - 3 ≤ t_4 - 4$ using \crefns{it:t12,it:torder}, thus $t_1 + t_3 ≤ t_4 - 4 + t_3$, together with $t_3 ≤ m - t_4$ (\cref{it:t34m}), leads to \cref{it:t13m}.
	\end{itemize}
\end{proof}

\begin{theorem}
	\label{th:boundsEquiv}
	$t \in T$ iff all the following hold:
	\begin{enumerate}[label=({\roman*}), ref={\roman*}]
		\item \label{it:t4NEW} $4 ≤ t_4 ≤ \frac{2 m - 2}{3}$;
		\item \label{it:t2NEW} $\max \set{2, t_4 - \khalf + 1, 2 t_4 - m + 1} ≤ t_2 ≤ \min \set{m - 1 - t_4, t_4 - 2, \khalf - 1}$;
		\item \label{it:t3NEW} $\max \set{t_2 + 1, t_4 - t_2 + 1} ≤ t_3 ≤ \min \set{\khalf, t_4 - 1, m - t_4}$;
		\item \label{it:t1NEW} $t_1 ≤ t_3 - (t_4 - t_2 + 1)$.
	\end{enumerate}
\end{theorem}
\begin{proof}[Sketch]
	For the forward direction, use the consequent bounds.
	For the backward direction, it should be easy.
	
	For the forward direction, we refer to results from \cref{th:consequentBounds} by their (arabic) item number.
	
	\Cref{it:t1423} is equivalent to $0 ≤ t_2 - t_1 - 2 - (t_4 - t_3 - 1)$ and from \cref{it:torder}, $0 ≤ t_4 - t_3 - 1$, thus $0 ≤ t_2 - t_1 - 2 + (t_4 - t_3 - 1)$.
	As $- t_1 ≤ 0$ and $t_2 - t_3 + 1 ≤ 0$ (from \cref{it:torder}), $0 ≤ - 2 + t_4 - 2$.
%	$4 ≤ 2 + t_1 + 2 ≤ t_2 + 2$ by \cref{it:t12}, with $t_2 + 2 ≤ t_3 + 1 ≤ t_4$ by \cref{it:torder}, yields $4 ≤ t_4$.
	From \cref{it:t1423}, $t_4 ≤ t_3 - t_1 + t_2 - 1$ and from \cref{it:torder}, $t_2 ≤ t_3 - 1$, whence, using $- t_1 ≤ 0$, $t_4 ≤ t_3  + t_3 - 2$, which also gives (together with \cref{it:t34m}, $t_3 ≤ m - t_4$) $t_4 ≤ 2 m - 2 t_4 - 2$, equivalently, \cref{it:t4NEW}.
\end{proof}

\begin{theorem}
	\label{th:delta}
	$\forall \prof \in \allprofs \suchthat \FBP \cap \MSP = \emptyset$, letting $\set{x} = \FBP$ and $\set{y} = \MSP$:
	\begin{equation}
		1 ≤ d(\lprof(x)) - d(\lprof(y)) ≤ \floor*{\frac{m - 1}{2}} - 2.
	\end{equation}
\end{theorem}
\begin{proof}
	Note that $d(\lprof(x)) - d(\lprof(y)) = (\max \lprof(x) - \min \lprof(x)) - (\max \lprof(y) - \min \lprof(y)) = \max \lprof(x) - \min \lprof(x) + \min \lprof(y) - \max \lprof(y)$.
	
	From \cref{th:equiv} \cref{it:ourMax}, $\max \lprof(x) - \min \lprof(x) ≤ \max \lprof(x) ≤ \floor{\frac{m - 1}{2}}$.
	From \cref{th:sufficientBounds} \cref{it:order}, $\min \lprof(y) < \max \lprof(x) < \max \lprof(y)$, thus $\min \lprof(y) + 2 ≤ \max \lprof(y)$ or equivalently, $\min \lprof(y) - \max \lprof(y) ≤ - 2$.

	Finally, from \cref{th:sufficientBounds} \cref{it:t1423}, $\min \lprof(x) + \max \lprof(y) + 1 ≤ \min \lprof(y) + \max \lprof(x)$.
\end{proof}

\subsection{Classifying profiles}
Let $T$, $C_{t, i}$ and $C_t$ be defined as in \cref{sec:classifying}.
Let $\mathscr{C} = \set{C_t \suchthat t \in T}$ denote the set of classes.

\begin{theorem}
	\label{th:B}
	$\forall t \in T, i \in N$:
	\begin{itemize}
		\item $\exists \prof \in C_{t, i} \suchthat \FBP = B(\prof)$;
		\item $t_1 = 1 ⇒ \exists \profD \in C_{t, i} \suchthat \FB(\profD) \subset B(\profD)$;
		\item $t_1 ≥ 2 ⇒ \exists \profD \in C_{t, i} \suchthat \FB(\profD) \cap B(\profD) = \emptyset$;
	\end{itemize}
\end{theorem}
\begin{proof}
	Let $t \in T$ and $i \in N$. We will refer to results from \cref{th:consequentBounds} by their item number.

	Name the alternatives $a_1, …, a_m$.
	Define $x = a_{t_1 + 1}$ and $y = a_{t_4 + 1}$.
	Define sequences of alternatives 
	\begin{description}
		\item[$A_1$] $(a_{t_4 + 2}, …, a_{t_2 + t_4 + 1})$;
		\item[$A_2$] $(a_{t_2 + t_4 + 2}, …, a_{t_3 + t_4})$ (with $A_2 = \emptyset$ iff $t_3 + t_4 < t_2 + t_4 + 2$);
		\item[$A_3$] $(a_{t_3 + t_4 + 1}, …, a_m)$;
		\item[$A_4$] $(a_1, …, a_{t_1})$;
		\item[$A_5$] $(a_{t_1 + 2}, …, a_{t_4})$.
	\end{description}
	Given a sequence $A$, define $A^{-1}$ as the inverse of $A$.
	Define $\prof$ as
	\begin{description}
		\item[$i$] $(a_1, …, a_m) = (A_4, x, A_5, y, A_1, A_2, A_3)$,
		\item[$\ibar$] $(A_1^{-1}, y, A_2, x, A_3, A_5, A_4^{-1})$
	\end{description}
	and define $\profD$ as
	\begin{description}
		\item[$i$] $(a_1, …, a_m) = (A_4, x, A_5, y, A_1, A_2, A_3)$,
		\item[$\ibar$] $(A_1^{-1}, y, A_2, x, A_4, A_3, A_5)$.
	\end{description}
	Note that $\prof$ and $\profD$ differ only by the position and ordering of $A_4$ in $\ibar$. Therefore, most of the facts we will establish for $\prof$ also hold, and can be established in a similar manner, for $\profD$.
	We will therefore reason in parallel for these two profiles in what follows.
	
	Note that $\prof(\ibar)$ and $\profD(\ibar)$ are indeed linear orders on $\allalts$, equivalently, list each alternative of $\allalts$ exactly once, as they are permutations of the sequence $(A_4, x, A_5, y, A_1, A_2, A_3)$ which lists each alternative of $\allalts$ exactly once. The latter fact holds because $t_2 + t_4 + 1 ≤ t_3 + t_4$, equivalently, $t_2 + 1 ≤ t_3$, from \cref{it:torder}.
	
	Observe that $t_1 = \lprof(x)_i = \lprofD(x)_i$ and $t_3 = \card{(A_1 \cup \set{y} \cup A_2)} = \lprof(x)_{\ibar} = \lprofD(x)_{\ibar}$. It follows that $\min \lprof(x) = \min \lprofD(x) = t_1$ and $\max \lprof(x) = \max \lprofD(x) = t_3$.
	Similarly, $t_4 = \lprof(y)_i = \lprofD(y)_i$ and $t_2 = \card{A_1} = \lprof(y)_{\ibar} = \lprofD(y)_{\ibar}$. It follows that $\min \lprof(y) = \min \lprofD(y) = t_2$ and $\max \lprof(y) = \max \lprofD(y) = t_4$.

	To see that $\FBP = \FB(\profD) = \argmin \max \lprof = \set{x}$, observe that $\max \lprof(x) = \max \lprofD(x) = t_3$ and let us show that $\forall z \in \allalts \setminus \set{x}: \max \lprof(z) > t_3 \land \max \lprofD(z) > t_3$. 
	Indeed:
	\begin{itemize}
		\item $\forall z \in \set{y} \cup A_1 \cup A_2 \cup A_3, t_3 < t_4 = \lprof(y)_i < \lprof(z)_i ≤ \max \lprof(z)$;
		\item $\forall z \in \set{y} \cup A_1 \cup A_2 \cup A_3, t_3 < t_4 = \lprofD(y)_i < \lprofD(z)_i ≤ \max \lprofD(z)$;
		\item $\forall z \in \set{A_4 \cup A_5}, t_3 = \lprof(x)_{\ibar} < \lprof(z)_{\ibar} ≤ \max \lprof(z)$;
		\item $\forall z \in \set{A_4 \cup A_5}, t_3 = \lprofD(x)_{\ibar} < \lprofD(z)_{\ibar} ≤ \max \lprofD(z)$.
	\end{itemize}
	
	To show that $\MSP = \MS(\profD) = \argmin_{\POP} (d \circ \lprof) = \set{y}$, observe that $y \in \POP$, $y \in \PO(\profD)$, $(d \circ \lprof)(y) = (d \circ \lprofD)(y) = t_4 - t_2$, and let us show that $\forall z \in \allalts \setminus \set{y}: (d \circ \lprof)(z) > t_4 - t_2 \land (d \circ \lprofD)(z) > t_4 - t_2$.
	\begin{itemize}
		\item $\forall z \in A_1$, $\lprof(z)_{\ibar} = \lprofD(z)_{\ibar} < \lprof(y)_{\ibar} < \lprof(y)_i < \lprof(z)_i = \lprofD(z)_i$ thus $d(\lprof(z)) = d(\lprofD(z)) > d(\lprof(y)) = t_4 - t_2$.
		\item $\forall z \in A_3$, $d(\lprofD(z)) = \max \lprofD(z) - \min \lprofD(z) = \card{(A_4 \cup \set{x} \cup A_5 \cup \set{y} \cup A_1 \cup A_2)} - \card{(A_1 \cup \set{y} \cup A_2 \cup \set{x} \cup A_4)} = \card{A_5} = t_4 - t_1 - 1 > t_4 - t_2$ 
			(using $t_1 + 1 < t_1 + 2 ≤ t_2$ from \cref{it:t12}).
		\item $\forall z \in A_3$, $d(\lprof(z)) = \card{(A_4 \cup A_5)} ≥ \card{A_5} > t_4 - t_2$ (from the previous line).
		\item $\forall z \in A_2$, $d(\lprof(z)) = d(\lprofD(z))> \card{A_5} > t_4 - t_2$.
		\item $\forall z \in A_5$, $d(\lprof(z)) = \max \lprof(z) - \min \lprof(z) = \abs{\card{(A_1 \cup \set{y} \cup A_2 \cup \set{x} \cup A_3)} - \card{(A_4 \cup \set{x})}} = \abs{\card{(A_1 \cup \set{y} \cup A_2 \cup A_3)} - \card{A_4}} = \abs{m - t_4 - t_1}$.
		And $m - t_4 - t_1 > m - t_4 - t_1 - 1 ≥ t_4 - t_2 > 0$, from \crefns{it:t1m42,it:torder}.
		\item $\forall z \in A_5$, $d(\lprofD(z)) = d(\lprof(z)) + \card{A_4} > t_4 - t_2$.
		\item $d(\lprof(x)) = d(\lprofD(x)) = t_3 - t_1 > t_3 - t_1 - 1 ≥ t_4 - t_2$ (using \cref{it:t4231}).
		\item $\forall z \in A_4$, $d(\lprof(z)) = \card{(A_1 \cup \set{y} \cup A_2 \cup \set{x} \cup A_3 \cup A_5)} - \card{A_4} > m - t_4 - t_1 > t_4 - t_2$ (from a previous line).
		\item $\forall z \in A_4$, $d(\lprofD(z)) = \card{(A_1 \cup \set{y} \cup A_2 \cup \set{x})} = t_3 + 1 > t_3 ≥ t_3 - t_1 > t_4 - t_2$ (from a previous line).
	\end{itemize}

	We see that $\prof \in \fprofs$ and $\profD \in \fprofs$ as it has already been established that $\forall z \in \allalts \setminus \set{y}: (d \circ \lprof)(z) > (d \circ \lprof)(y) \land (d \circ \lprofD)(z) > (d \circ \lprofD)(y)$.

	Finally, we turn to the Borda winners. 
	Observe that $\sum \lprof(x) = t_1 + t_3$. 
	Let us show first that $\forall z \in \allalts \setminus (A_4 \cup \set{x}): \sum \lprof(z) > t_1 + t_3 \land \sum \lprofD(z) > t_1 + t_3$. 
	\begin{itemize}
		\item $\forall z \in A_1$, $\sum \lprof(z) = \sum \lprofD(z) = \card{(A_4 \cup \set{x} \cup A_5 \cup \set{y} \cup A_1 \setminus \set{z})} = t_4 + 1 + t_2 - 1 = t_2 + t_4 > t_1 + t_3$.
		\item $\forall z \in \set{y} \cup A_2 \cup A_3$, $\sum \lprof(z) ≥ \sum \lprof(y) = t_2 + t_4 > t_1 + t_3$.
		\item $\forall z \in \set{y} \cup A_2 \cup A_3$, $\sum \lprofD(z) ≥ \sum \lprofD(y) = t_2 + t_4 > t_1 + t_3$.
	\end{itemize}

	To see that $B(\prof) = \argmin \sum \lprof = \set{x}$, observe furthermore that
	$\forall z \in A_4$, $\sum \lprof(z) ≥ \card{(A_1 \cup \set{y} \cup A_2 \cup \set{x} \cup A_3 \cup A_5 \cup A_4 \setminus \set{z})} = \card{\allalts \setminus \set{z}} = m - 1 > m - 4 ≥ t_1 + t_3$ (using \cref{it:t13m}).
	
	Only remains to consider $B(\profD)$.
	We know from above that $A_4$ and $x$ are the only candidates. Thus, $B(\profD) \subseteq \set{a_1, x}$. (Note that $a_1 ≠ x ⇔ t_1 ≥ 1 ⇔ A_4 ≠ \emptyset ⇔ \prof ≠ \profD$.)
	We see that $\sum \lprofD(a_1) - \sum \lprofD(x) = (\lprofD(a_1)_i - \lprofD(x)_i) + (\lprofD(a_1)_{\ibar} - \lprofD(x)_{\ibar}) = - \card{A_4} + 1 = 1 - t_1$.
	Thus, if $t_1 = 1$, $B(\profD) = \set{a_1, x}$ and if $t_1 ≥ 2$, $B(\profD) = \set{a_1}$.
\end{proof}

\begin{example}
Here is an example construction of a profile $\prof$ as in the proof of \cref{th:B}, with $m = 13$ and $t_1 = \lprof(x)_i = 1$; $t_2 = \lprof(y)_{\ibar} = 4$; $t_3 = \lprof(x)_{\ibar} = 5$; $t_4 = \lprof(y)_i = 6$; thus $\sum \lprof(y) = 10$, $x = \bm{b}$ and $y = \boxed{g}$.
	\begin{description}
		\item[$A_1$] $(a_8, …, a_{11}) = (h, i, j, k)$;
		\item[$A_2$] $(a_{12}, …, a_{11}) = \emptyset$;
		\item[$A_3$] $(a_{12}, …, a_{13}) = (l, m)$;
		\item[$A_4$] $(a_1, …, a_1) = (a)$;
		\item[$A_5$] $(a_3, …, a_6) = (c, d, e, f)$.
	\end{description}
  \begin{equation}
    \begin{array}{*{13}c}
      a&\bm{b}&c&d&e&f&\boxed{g}&h&i&j&k&l&m\\
      k&j&i&h&\boxed{g}&\bm{b}&l&m&a&c&d&e&f
    \end{array}
  \end{equation}
\end{example}

\begin{theorem}
	\label{th:cover}
	The set of classes $\set{C_t \suchthat t \in T}$ is a complete and disjoint cover of $\fprofs$. 
	Furthermore, given any $t \in T$, no class $C_t$ is empty.
\end{theorem}
\begin{proof}
	First, it is a complete cover, formally, $\fprofs = \bigcup \set{C_t \suchthat t \in T}$: from \cref{th:sufficientBounds}, $\forall \prof \in \fprofs, \exists t \in T \suchthat \prof \in C_t$; and conversely, $\forall t \in T, \prof \in C_t$, it follows from the definitions that $\prof \in \fprofs$.
	
	Second, that the classes are disjoint, formally, $C_t \cap C_{t'} ≠ \emptyset ⇒ t = t'$, can be seen as follows. 
	Consider any $\prof \in C_t$, let $\set{x} = \FBP$ and $\set{y} = \MSP$ and pick any $i \suchthat \prof \in C_{t, i}$. 
	By definition of $C_{t, i}$, $\lprof(x)_i = t_1 < \lprof(y)_{\ibar} = t_2 < \lprof(x)_{\ibar} = t_3 < \lprof(y)_i = t_4$. 
	It follows that $\prof \notin C_{t', \ibar}$ (as the latter requires $\lprof(x)_{\ibar} = t'_1 < \lprof(x)_i = t'_3$).
	Therefore, if $\prof \in C_{t'}$, then $\prof \in C_{t', i}$, thus $\lprof(x)_i = t'_1, \lprof(y)_{\ibar} = t'_2, \lprof(x)_{\ibar} = t'_3$ and $\lprof(y)_i = t'_4$, whence $t = t'$.
	
	Finally, \cref{th:B} proves that no $C_t$ is empty.
\end{proof}

\subsection{Borda}
\begin{theorem}
	\label{th:min0B}
	$\forall \prof \in \allprofs: [\exists x \in FB(P) \suchthat \min \lprof(x) = 0] ⇒ B(P) \subseteq FB(P)$.
\end{theorem}
\begin{proof}
	Consider any $z \in B(P)$. 
	Observe that $\sum \lprof(z) ≤ \sum \lprof(x)$, thus, $\max \lprof(z) ≤ \max \lprof(z) + \min \lprof(z) = \sum \lprof(z) ≤ \sum \lprof(x) = \max \lprof(x)$.
	It follows that $z \in FB(P)$.
\end{proof}
\begin{theorem}
	\label{th:BMS}
	$\forall \prof \in \allprofs: \MSP \nsubseteq \FBP ⇒ \MSP \cap B(P) = \emptyset$.
\end{theorem}
\begin{proof}
	Consider any $y \in \MSP$ and let us show that $y \notin \argmin \sum \lprof = B(\prof)$.
	Pick any $x \in \FBP$ (thus $\max \lprof(x) = \min \max \lprof$).
	
	As $\MSP \nsubseteq \FBP$, $y \notin \FBP$, thus $\max \lprof(x) = \min \max \lprof < \max \lprof(y)$.
	
	We furthermore deduce that $\min \lprof(y) ≥ \min \lprof(x)$, otherwise, $\min \lprof(y) < \min \lprof(x) ≤ \max \lprof(x) = \min \max \lprof < \max \lprof(y)$ hence $y \notin \MSP = \argmin_{\POP}(d \circ \lprof)$ (using $x \in \FBP ⇒ x \in \POP$).
	
	It follows that $\sum \lprof(x) < \sum \lprof(y)$.
\end{proof}
\begin{theorem}
	\label{th:min1B}
	$\forall \prof \in \allprofs: [\exists x \in \FBP \suchthat \min \lprof(x) = 1] ⇒ \FBP \cap B(P) ≠ \emptyset$.
\end{theorem}
\begin{proof}
	Considering any $z \notin \FBP$, let us show that $\sum \lprof(x) ≤ \sum \lprof(z)$ (which excludes $\argmin \sum \lprof \cap \FBP = \emptyset$).
	As $x \in \FBP$, $\max \lprof(x) = \min \max \lprof$.
	If $\max \lprof(z) = \min \max \lprof$ then $z \in \FBP$, thus, $\max \lprof(z) > \max \lprof(x)$, equivalently, $\max \lprof(x) + 1 ≤ \max \lprof(z)$.
	Then $\sum \lprof(x) = \min \lprof(x) + \max \lprof(x) = 1 + \max \lprof(x) ≤ \max \lprof(z) ≤ \sum \lprof(z)$.
\end{proof}

\begin{remark}
	\label{rk:BFB}
	Here are the possible relationships between $B(\prof)$ and $\FBP$, considering $\prof \in \fprofs$ (thus $\MSP \nsubseteq \FBP$, with $\FBP = \set{x}$):
	\begin{itemize}
		\item if $\min \lprof(x) = 0$, $B(\prof) = \FBP$ (\cref{th:min0B});
		\item if $\min \lprof(x) = 1$, $x \in B(\prof)$ (\cref{th:min1B}), with both $\FBP = B(\prof)$ and $\FBP \subset B(\prof)$ possible (\cref{th:B});
		\item if $\min \lprof(x) ≥ 2$, both $\FBP = B(\prof)$ and $\FBP \cap B(\prof) = \emptyset$ are possible (\cref{th:B}).
	\end{itemize}
\end{remark}

\subsection{Bounds}
\begin{theorem}
	\label{th:boundsSummary}
	$\forall \prof \in \allprofs \suchthat \FBP \cap \MSP = \emptyset$, letting $\set{x} = \FBP$, $\set{y} = \MSP$ and $\set{i} = \argmax \lprof(y)$, and defining $t_1 = \min \lprof(x)$, $t_2 = \min \lprof(y)$, $t_3 = \max \lprof(x)$ and $t_4 = \max \lprof(y)$:
	\begin{enumerate}
		\item \label{it:t4} $4 ≤ t_4 ≤ \frac{2 m - 2}{3}$;
		\item \label{it:t2} $\max \set{2, t_4 - \khalf + 1, 2 t_4 - m + 1} ≤ t_2 ≤ \min \set{m - 1 - t_4, t_4 - 2, \khalf - 1}$;
		\item \label{it:t3} $\max \set{t_2 + 1, t_4 - t_2 + 1} ≤ t_3 ≤ \min \set{\khalf, t_4 - 1, m - t_4}$;
		\item \label{it:t1} $t_1 ≤ t_3 - (t_4 - t_2 + 1)$.
	\end{enumerate}
\end{theorem}
\begin{proof}

\end{proof}

\begin{theorem}
	\label{th:allBounds}
	$\forall \prof \in \allprofs \suchthat \MSP \nsubseteq \FBP$:
	\begin{enumerate}
		\item \label{it:minYUSumVOLD} $\min \lprof(y) ≤ m - 1 - \max \lprof(y)$;
		\item \label{it:maxXUMaxCVOLD} $\max \lprof(x) ≤ m - \max \lprof(y)$;
		\item \label{it:minXUVOLD} $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y) + 1)$;
		\item \label{it:maxYUVOLD} $\max \lprof(y) ≤ \frac{2 m - 2}{3}$;
		\item \label{it:maxXUMVOLD} $\max \lprof(x) ≤ \floor{\frac{m - 1}{2}}$;
		\item \label{it:maxXLVOLD} $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$;
		\item \label{it:minYLVOLD} $\max \lprof(y) - \floor{\frac{m - 1}{2}} + 1 ≤ \min \lprof(y)$;
		\item \label{it:minYUMVOLD} $\min \lprof(y) ≤ \floor{\frac{m - 1}{2}} - 1$;
		\item \label{it:maxXUMaxVOLD} $\max \lprof(x) ≤ \max \lprof(y) - 1$;
		\item \label{it:maxXLMinVOLD} $\min \lprof(y) + 1 ≤ \max \lprof(x)$;
		\item \label{it:minYUMaxVOLD} $\min \lprof(y) ≤ \max \lprof(y) - 2$;
		\item \label{it:minYL2VOLD} $2 ≤ \min \lprof(y)$;
		\item \label{it:maxYLVOLD} $4 ≤ \max \lprof(y)$;
		\item \label{it:minYLCVOLD} $2 \max \lprof(y) - m + 1 ≤ \min \lprof(y)$;
		\item \label{it:deltaVOLD} $d(\lprof(x)) - d(\lprof(y)) ≤ \floor{\frac{m - 1}{2}} - 2$.
	\end{enumerate}
\end{theorem}
\begin{proof}
From \cref{th:rhoMinOLD} \cref{it:singVCOLD}, $\card{\argmax \lprof(x)} = \card{\argmax \lprof(y)} = 1$, thus we can define $\argmax \lprof(x) = \set{\ibar}$. Furthermore, $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$ as per \cref{th:rhoMinOLD} \cref{it:singVbisOLD}, thus, we can define $\argmax \lprof(y) = \set{i}$. 

Note that $\forall \prof \in \allprofs, z \in \POP: \sum \lprof(z) ≤ m - 1$.
In particular, $y \in PE$ requires $\sum \lprof(y) ≤ m - 1$, equivalently, \cref{it:minYUSumOLD}.

From \cref{th:rhoMinOLD} \cref{it:rhoMinOLD}, $\forall w \succ_i y: x \succeq_{\ibar} w$.
Also, by definition of $\lprof$, $\card{{\prefto_i}(y)} = \lprof(y)_i$.
We obtain $\lprof(x)_{\ibar} ≤ m - \lprof(y)_i$, or equivalently by definition of $i$ and $\ibar$, \cref{it:maxXUMaxCOLD}.

As $(d \circ \lprof)(y) < (d \circ \lprof)(x)$ (equivalently, $(d \circ \lprof)(y) + 1 ≤ (d \circ \lprof)(x)$), we obtain \cref{it:minXUOLD}.

From \cref{it:minXUOLD}, $\max \lprof(y) ≤ \max \lprof(x) - \min \lprof(x) + \min \lprof(y) - 1$, whence, using \cref{it:minYUSumOLD,it:maxXUMaxCOLD} and $- \min \lprof(x) ≤ 0$, $\max \lprof(y) ≤ m - \max \lprof(y) + m - 1 - \max \lprof(y) - 1$, equivalently, \cref{it:maxYUOLD}.

%Observe that $\exists z \in \allalts \suchthat \lprof(z)_i ≤ \khalf \land \lprof(z)_{\ibar} ≤ \khalf$. That’s because $\card \set{z \in \allalts \suchthat \lprof(z)_i ≤ \khalf} = \khalf + 1$ and there are only $\card \set{z \in \allalts \suchthat \lprof(z)_{\ibar} > \khalf} = m - (\khalf + 1) = \floor{\frac{m - 1}{2}} < \khalf + 1$ positions that do not satisfy $\lprof(z)_{\ibar} ≤ \khalf$.
%It follows that $\argmin \max \lprof ≤ \khalf$, which establishes \cref{it:maxXUMOLD}.
\Cref{it:maxXUMOLD} is established by \cref{th:equivOLD} \cref{it:rhoOLD}.

Combining \cref{it:minXUOLD} with $0 ≤ \min \lprof(x)$ establishes \cref{it:maxXLOLD}. 

Combining \cref{it:maxXUMOLD,it:maxXLOLD},
we get \cref{it:minYLOLD}.
%Using $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y)) - 1$, equivalently, $\min \lprof(x) + \max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$ together with $0 ≤ \min \lprof(x)$ yields $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$.

Combining \cref{it:minYLOLD} with $0 ≤ \max \lprof(y)$ establishes \cref{it:minYUMOLD}. 
%Also, $\min \lprof(y) < \max \lprof(x)$ by ordering, equivalently $\min \lprof(y) ≤ \max \lprof(x) - 1$, and $\max \lprof(x) ≤ \khalf$, thus $\min \lprof(y) ≤ \khalf - 1$.

By \cref{th:rhoMinOLD} \cref{it:orderOLD}, $\max \lprof(x) < \max \lprof(y)$, equivalently, \cref{it:maxXUMaxOLD}.

Similarly, by \cref{th:rhoMinOLD} \cref{it:orderOLD}, $\min \lprof(y) < \max \lprof(x)$, equivalently, \cref{it:maxXLMinOLD}.

Combining \cref{it:maxXUMaxOLD,it:maxXLMinOLD} yields \cref{it:minYUMaxOLD}.

From \cref{it:maxXLOLD,it:maxXUMaxOLD},
%Also, from $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x) ≤ \max \lprof(y) - 1$, thus 
$\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(y) - 1$, whence \cref{it:minYL2OLD}.

Also, \cref{it:minYUMaxOLD,it:minYL2OLD} lead to \cref{it:maxYLOLD}.

\Cref{it:maxXUMaxCOLD,it:maxXLOLD} lead to \cref{it:minYLCOLD}.

Finally, from $\max \lprof(x) - \min \lprof(x) ≤ \max \lprof(x) ≤ \floor{\frac{m - 1}{2}}$ (\cref{it:maxXUMOLD}) and $- (\max \lprof(y) - \min \lprof(y)) ≤ -2$ (\cref{it:minYUMaxOLD}), we obtain \cref{it:deltaOLD}.
\end{proof}

\subsection{Tightness results}
The following two theorems illustrate why we cannot obtain the results that were obtained above with the hypothesis $\FBP \cap \MSP = \emptyset$ by using merely an hypothesis of non inclusion.

\begin{theorem}
	\label{th:FBMSposs}
	For any $m ≥ 6$, $\FBP \cap \MSP ≠ \emptyset \not⇒ \MSP \subseteq \FBP$.
	In other words, $\exists \prof \suchthat \FBP \cap \MSP ≠ \emptyset \land \MSP \nsubseteq \FBP$.
	In supplement, $\exists \prof \suchthat \FBP \cap \argmin_{\allalts}(d \circ \lprof)  ≠ \emptyset \land \argmin_{\allalts}(d \circ \lprof) \nsubseteq \FBP$.
\end{theorem}
\begin{proof}
	In the following profile $\prof$,
	\begin{equation}
		\begin{array}{*{13}l}
			a	& b	& c	& d	& e	& f	& \ldots\\
			e& d& a &f &b &c &…
		\end{array},
	\end{equation}
	$\FBP = \argmin \max \lprof = \set{a}$ and $\MSP = \argmin_{\POP}(d \circ \lprof) = \argmin_{\allalts}(d \circ \lprof) = \set{a, d}$.
\end{proof}

\begin{theorem}
	\label{th:MSFBposs}
	For any $m ≥ 4$, $\FBP \cap \MSP ≠ \emptyset \not⇒ \FBP \subseteq \MSP$.
\end{theorem}
\begin{proof}
	In the following profile $\prof$,
	\begin{equation}
		\begin{array}{*{13}l}
			a	& c	& b	& d	& \ldots\\
			d& b& a &c &…
		\end{array},
	\end{equation}
	$\FBP = \argmin \max \lprof = \set{a, b}$ and $\MSP = \argmin_{\POP}(d \circ \lprof) = \argmin_{\allalts}(d \circ \lprof) = \set{b}$.
\end{proof}

\section{Outdated results}
The results below are replaced by the above ones or are not used any more. Moreover, some of them seem wrong so the proofs should be checked carefully if we want to use them.

Define $\rho_\prof = \min_\allalts \max \lprof$.
(We often use simply $\rho$ when the profile considered is clear.)
Let ${\prefto_i}(z)$ designate the alternatives better than $z$ for voter $i$.
\begin{theorem}
	\label{th:fourfactsOLD}
Consider any profile $\prof \in \allprofs$. Pick any $x \in \FBP$. Pick any $i \in N$ such that $\lprofi[x] = \min\lprof(x)$ and define $\ibar$ as the other individual, thus with $\lprofibar[x] = \max\lprof(x) = \rho$. Define $z$ as the alternative such that $\lprofi[z] = \rho$.
	Then, the following facts hold.
	\begin{enumerate}
		\item \label{it:rhoLargeOLD} $\rho ≤ \frac{m}{2}$.
		\item \label{it:rhoStrictOLD} If $\rho = \frac{m}{2}$, then $\FBP = \set{x, z}$. 
		\item \label {it:notXYOLD} If $\FBP = \set{x, z}$, then $\minineq[\FBP] = \minineq[\POP]$. 
		\item If $\minineq[\FBP] ≤ 2$, then $\minineq[\FBP] = \minineq[\POP]$.
	\end{enumerate}
\end{theorem}
\begin{proof}
 	\emph{First fact}
 	
	Define $S_1 = \set{y ≠ x \suchthat 0 ≤ \lprofi[y] < \rho}$ and $S_2 = \set{y \suchthat \rho < \lprofibar[y] ≤ m - 1}$.
 	By definition of $\rho$, $\nexists y \suchthat \max\lprof(y) < \rho$,
	thus, $\forall y: [\lprofi[y] < \rho \land \lprofibar[y] ≠ \rho] ⇒ \rho < \lprofibar[y]$.
	Because $x ≠ y ⇒ \lprofibar[y] ≠ \rho$ (as $\lprofibar[x] = \rho$), we obtain that $S_1 \subseteq S_2$.
	Because $\card{\set{y \suchthat 0 ≤ \lprofi[y] < \rho}} = \rho$, $\card{S_1} ≥ \rho - 1$.
	It follows that $\card{S_2} ≥ \rho - 1$.
	Also, $\card{S_2} = m - 1 - \rho$. We obtain $m - 1 - \rho ≥ \rho - 1$, thus $\rho ≤ \frac{m}{2}$.
	
	\emph{Second fact}
	
	Pursuing with $S_1$ and $S_2$ as defined above, and assuming further that $\rho = \frac{m}{2}$, or equivalently $m - \rho = \rho$, we see that $S_1$ and $S_2$ have the same cardinalities, hence, are equal. By definition of $z$, $z \notin S_1$. Thus, $z \notin S_2$. Therefore, $\lprofibar[z] ≤ \rho$, and as $\lprofi[z] = \rho$, $z \in \FBP$. As $\FBP = \set{y \suchthat \max\lprof(y) = \rho}$, $y \in \FBP$ requires that $\lprofi[y] = \rho$ or $\lprofibar[y] = \rho$, thus, no alternative but $x$ and $z$ may be in $\FBP$.
	
	\emph{Third fact}
	
	Assuming now that $\FBP = \set{x, z}$, and picking any $y \in \POP$, let us show that $\ineq(y) ≥ \minineq[\FBP]$.
	By hypothesis, $\lprofibar[z] ≤ \rho$ and $\lprofi[x] ≤ \rho$.
	Now if $\rho < \lprofi[y]$, then $\lprofibar[y] < \lprofibar[z]$ (otherwise $z$ Pareto dominates $y$, as $\lprofi[z] = \rho$), whence $\ineq(y) > \ineq(z)$ as $\lprofibar[y] < \lprofibar[z] ≤ \lprofi[z] = \rho < \lprofi[y]$.
	Similarly, assuming that $\rho < \lprofibar[y]$ yields that $\ineq(y) > \ineq(x)$.
	The only remaining possibility is that $\lprofi[y] ≤ \rho$ and $\lprofibar[y] ≤ \rho$, in which case $y \in \FBP$.
	
	\emph{Fourth fact}
	
	Assuming that $\minineq[\FBP] ≤ 2$, and picking any $y \in \POP$, let us show that $\ineq(y) ≥ \minineq[\FBP]$.
	If $\rho < \lprofi[y]$, then $\lprofi[x] < \lprofi[y]$ and $\lprofibar[x] < \lprofi[y]$, thus $\lprofibar[y] < \lprofibar[x]$ (otherwise $x$ Pareto dominates $y$), thus $\lprofibar[y] < \lprofibar[x] < \lprofi[y]$, thus $\ineq(y) ≥ 2$.
	If $\rho < \lprofibar[y]$, an identical reasoning, exchanging $i$ and $\ibar$, concludes identically.
	Otherwise, $y \in \FBP$.
 \end{proof}

\begin{corollary}
	\label{th:morethan6OLD}
 	For $m ≤ 6$, FB satisfies PCC for the inequality relation $d$.
\end{corollary}
\begin{proof}
	Using \cref{th:maxFB}, $\min \max \lprof ≤ 3$, and suffices then to use either, if $\min \max \lprof = 3$, the second and the third facts, or otherwise, the fourth fact of \cref{th:fourfactsOLD} (because $\minineq[\FBP] ≤ \rho$) to prove as required that some alternative in $\FBP$ reaches the required minimal inequality over the Pareto optimal alternatives.
\end{proof}

\begin{corollary}
	\label{th:conds}
	The profiles such that $\minineq[\FBP] ≠ \minineq[\POP]$ must satisfy all the following conditions. Let $x \in \FBP$.
	\begin{itemize}
		\item $\card{\FBP} = 1$.
		\item $3 ≤ \ineq(x) ≤ \rho < \frac{m}{2}$ (whence $m ≥ 7$).
		\item $2 ≤ \minineq[\POP] < \ineq(x)$.
	\end{itemize}
\end{corollary}
\begin{proof}
	We see that these conditions are required using \cref{th:fourfactsOLD} and \cref{th:morethan6OLD}: $\FBP$ must be a singleton because of the third fact; $3 ≤ \ineq(x)$ because of the fourth fact; and $\rho < \frac{m}{2}$ because of the first and second facts.
\end{proof}

\begin{lemma}
	\label{th:maxNope}
	$[\max \set{y_1, y_2} - \min \set{y_1, y_2} ≤ x_2 - x_1]$ implies $[y_2 - y_1 ≤ x_2 - x_1]$.
\end{lemma}
\begin{proof}
	If $\max \set{y_1, y_2} = y_2$, this is immediate, and otherwise, $y_2 - y_1 ≤ y_1 - y_2$ and $y_1 - y_2 ≤ x_2 - x_1$ hence $y_2 - y_1 ≤ x_2 - x_1$.
\end{proof}

\begin{lemma}
	\label{th:eqToEq}
	$[y_2 - y_1 ≤ x_2 - x_1 \land x_1 ≤ y_1 ⇔ y_2 ≤ x_2]$ is equivalent to $[y_2 - y_1 ≤ x_2 - x_1 \land x_1 ≤ y_1 \land y_2 ≤ x_2]$ and equivalent to $[x_1 ≤ y_1 \land y_2 ≤ x_2]$.
\end{lemma}
\begin{proof}
	From the left hand side, $y_2 > x_2$ implies $x_1 > y_1$ hence $y_2 - y_1 > x_2 - x_1$, excluded; thus, $y_2 ≤ x_2$, hence, $x_1 ≤ y_1$. From the right hand side, $y_2 + x_1 ≤ x_2 + y_1$.
\end{proof}

\begin{lemma}
	\label{th:simpleImpl}
	$[y_2 - y_1 ≤ x_2 - x_1 \land x_1 < y_1 ⇒ y_2 < x_2]$ implies that $x_2 ≥ y_2$.
\end{lemma}
\begin{proof}
	If $x_1 < y_1$, done; otherwise, $x_1 ≥ y_1$, equivalently, $x_1 - y_1 ≥ 0$, and we know $x_2 - y_2 ≥ x_1 - y_1$ thus $x_2 - y_2 ≥ 0$ whence $x_2 ≥ y_2$.
\end{proof}

\begin{theorem}
	\label{th:equivOLD}
	The following propositions are equivalent:
	\begin{enumerate}
		\item \label{it:bigYOLD} $\exists y \in \MSP \suchthat \max \lprof(y) > \rho$;
		\item \label{it:allBigYOLD} $\forall y \in \MSP: \max \lprof(y) > \rho$;
		\item \label{it:noIntersOLD} $\FBP \cap \MSP = \emptyset$;
		\item \label{it:notSubsOLD} $\MSP \nsubseteq \FBP$.
	\end{enumerate}
	Furthermore, they imply:
	\begin{enumerate}[label=({\roman*}), ref={\roman*}]
		\item \label{it:card1OLD} $\card{\FBP} = 1$;
		\item \label{it:dispMinOLD} Letting $\FBP = \set{x}$, we have that $\forall \ibar \in \argmax \lprof(x): \MSP = \max \restr{{\pref_i}}{{\prefto_{\ibar}}(x)}$;
		\item \label{it:singMSOLD} $\card{\MSP = 1}$;
		\item \label{it:paretoOLD} Letting furthermore $\MSP = \set{y}$, we have that $\forall i \in \argmax \lprof(y): [x \pref_i y \land y \pref_{\ibar} x]$;
%		\item $\exists w \suchthat \min \lprof(w) = \rho < \max \lprof(w)$;
		\item \label{it:ordMinYOLD} $\min \lprof(x) < \min \lprof(y)$;
		\item \label{it:singVOLD} $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$ (in words: the voter that maximizes $\lprof(x)$ differs from the one that maximizes $\lprof(y)$);
		\item \label{it:singVcontrastOLD} $\forall i \in N: [i \in \argmax \lprof(y) ⇔ \ibar \in \argmax \lprof(x)]$;
		\item \label{it:rhoOLD} $\rho < \frac{m}{2}$.
	\end{enumerate}
\end{theorem}
\begin{proof}
Pick any $y \in \MSP = \argmin_{\POP} (d \circ \lprof)$, $x \in \FBP = \argmin \max \lprof$ and $\ibar \in \argmax \lprof(x)$.

From \cref{th:FBPO}, any by definition of $y$, $x, y \in \POP$.
Thus $\lprof(y)_i < \lprof(x)_i ⇔ \lprof(y)_{\ibar} > \lprof(x)_{\ibar}$. 

Also, $(d \circ \lprof)(y) ≤ (d \circ \lprof)(x)$, equivalently, $\max \lprof(y) - \min \lprof(y) ≤ \lprof(x)_{\ibar} - \lprof(x)_i$.

Using \cref{th:maxNope,th:eqToEq}, these two claims imply that $\lprof(y)_{\ibar} ≤ \lprof(x)_{\ibar} = \rho \land \lprof(x)_i ≤ \lprof(y)_i$.

By definition of $\rho$, $\max \lprof(y) ≥ \rho$. We obtain $\lprof(y)_{\ibar} ≤ \lprof(x)_{\ibar} = \rho ≤ \max \lprof(y) \land \lprof(x)_i ≤ \lprof(y)_i$.

Pick any $y' \in \MSP \suchthat \max \lprof(y') > \rho$, and let us show that $y' \in \argmin_{\set{w \suchthat \lprof(w)_{\ibar} < \rho}} \lprof(w)_i$. 

Note that our conclusions so far concerning $y$ apply to $y'$.
By our assumption that $\rho < \max \lprof(y')$, $\max \lprof(y') = \lprof(y')_i$.
Pick any $w$ such that $\lprof(w)_{\ibar} < \rho$.
Because $y'$ is not Pareto-dominated by $w$, $\lprof(w)_{\ibar} < \lprof(y')_{\ibar} ⇒ \lprof(w)_i > \lprof(y')_i$. 
By definition of $\rho$, $\max \lprof(w) ≥ \rho$. Thus, $\lprof(w)_i ≥ \rho > \lprof(w)_{\ibar}$.
Also, $y'$ has smallest spread; formally, $\max \lprof(y') - \min \lprof(y') ≤ \lprof(w)_i - \lprof(w)_{\ibar}$.
\Cref{th:maxNope,th:simpleImpl} yield that $\lprof(w)_i ≥ \lprof(y')_i$, which proves that $\MSP \subseteq  \argmin_{\set{w \suchthat \lprof(w)_{\ibar} < \rho}} \lprof(w)_i$.

As $1 ≤ \card{\MSP} ≤ \card{\argmin_{\set{w \suchthat \lprof(w)_{\ibar} < \rho}} \lprof(w)_i} = 1$, this suffices to establish that $\ref{it:bigYOLD} ⇒ \ref{it:card1OLD}$ and $\ref{it:bigYOLD} ⇒ \ref{it:dispMinOLD}$.

We have shown that $\card{\MSP} = 1$, thus, \ref{it:bigYOLD} ⇒ \ref{it:allBigYOLD} and \ref{it:allBigYOLD} ⇒ \ref{it:bigYOLD}.

$\card{\MSP} = 1$ and we see from $\max \lprof(y') > \rho$ that $y' \notin \FBP$, therefore obtaining $\ref{it:bigYOLD} ⇒ \ref{it:noIntersOLD}$. 

The implication $\ref{it:noIntersOLD} ⇒ \ref{it:notSubsOLD}$ is immediate as $\MSP ≠ \emptyset$.

Starting now from $\ref{it:notSubsOLD}$, and picking any $y \in \MSP$, we know $y \notin \FBP$; but this requires $\rho < \max \lprof(y)$, by definition of $\FB$. This establishes $\ref{it:notSubsOLD} ⇒ \ref{it:bigYOLD}$.

\Cref{it:singMSOLD} follows from \cref{it:dispMinOLD}.

Considering \cref{it:paretoOLD},	we know that $\max \lprof(x) < \max \lprof(y)$ from \cref{it:bigYOLD}. 
As $\min \lprof(x) ≤ \max \lprof(x)$, it follows that $x \pref_i y$.
As $y \in POP$, we cannot have $x \pref_{\ibar} y$, thus, $y \pref_{\ibar} x$.

Considering \cref{it:ordMinYOLD}, by \cref{it:bigYOLD}, $\max \lprof(x) < \max \lprof(y)$.
Note that $\min \lprof(y) ≤ \min \lprof(x)$ would lead to the ordering $\min \lprof(y) ≤ \min \lprof(x) ≤ \max \lprof(x) < \max \lprof(y)$, contradicting $(d \circ \lprof)(y) < (d \circ \lprof)(x)$, thus, $\min \lprof(x) < \min \lprof(y)$.

Considering \cref{it:singVOLD}, assume that $\exists i \in \argmax \lprof(x) \cap \argmax \lprof(y)$. Thus, $\lprof(x)_i = \max \lprof(x)$ and $\max \lprof(y) = \lprof(y)_i$, whence $\lprof(y)_{\ibar} = \min \lprof(y)$ and $\min \lprof(x) = \lprof(x)_{\ibar}$.
	From \cref{it:paretoOLD}, $y \pref_{\ibar} x$.
	Thus $\lprof(y)_{\ibar} = \min \lprof(y) < \min \lprof(x) = \lprof(x)_{\ibar}$, which contradicts $\min \lprof(y) > \min \lprof(x)$, and thus establishes that $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$.
	
	It follows from $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$ that $\forall i \in N: [i \in \argmax \lprof(y) ⇔ \ibar \in \argmax \lprof(x)]$ (\cref{it:singVcontrastOLD}).

	Finally, \cref{th:fourfactsOLD} \cref{it:rhoStrictOLD,it:notXYOLD} and this Theorem \cref{it:notSubsOLD} yield $\rho ≠ \frac{m}{2}$ (TODO establish that $x ≠ z$ using $\min \lprof(x) ≠ \max \lprof(x)$) which together with \cref{th:fourfactsOLD} \cref{it:rhoLargeOLD} yields \cref{it:rhoOLD}.
\end{proof}

\begin{corollary}
	\label{th:rhoMinOLD}
	If $\MSP \nsubseteq \FBP$:
	\begin{enumerate}
		\item $\card{\FBP} = 1$;
		\item \label{it:singVCOLD} $\card{\argmax \lprof(x)} = \card{\argmax \lprof(y)} = 1$;
		\item \label{it:singVbisOLD} $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$;
		\item \label{it:rhoMinOLD} Letting $\FBP = \set{x}$, $\MSP = \set{y}$, $\argmax \lprof(x) = \set{\ibar}$, we have that $\forall w \succ_i y: x \succeq_{\ibar} w$;
		\item \label{it:orderOLD} Letting furthermore $\argmax \lprof(y) = \set{i}$ (thanks to \cref{it:singVbisOLD}), we have that $\lprof(x)_i = \min \lprof(x) < \lprof(y)_{\ibar} = \min \lprof(y) < \lprof(x)_{\ibar} = \max \lprof(x) < \lprof(y)_i = \max \lprof(y)$.
	\end{enumerate}
\end{corollary}
\begin{proof}
	\Cref{it:singVCOLD} follows from (and \cref{it:singVbisOLD} repeats) \cref{th:equivOLD} \cref{it:singVOLD}.
	\Cref{it:rhoMinOLD} also follows from \cref{th:equivOLD} \cref{it:dispMinOLD} which states that $y$ is the best-for-$i$ alternative among the better-than-$x$ for $\ibar$: contrapositively, any alternative better than $y$ for $i$ cannot be among the better than $x$ for $\ibar$.
	Turning to \cref{it:orderOLD}, by definition of $i$ and $\ibar$, $\lprof(x)_{\ibar} = \max \lprof(x)$ and $\lprof(y)_i = \max \lprof(y)$, thus, $\lprof(x)_i = \min \lprof(x)$ and $\lprof(y)_{\ibar} = \min \lprof(y)$; by \cref{th:equivOLD} \cref{it:bigYOLD}, $\max \lprof(x) < \max \lprof(y)$; by \cref{th:equivOLD} \cref{it:paretoOLD}, $\lprof(y)_{\ibar} < \lprof(x)_{\ibar}$; and by \cref{th:equivOLD} \cref{it:ordMinYOLD}, $\min \lprof(x) < \min \lprof(y)$.
\end{proof}

\begin{theorem}
	\label{th:allBoundsOLD}
	$\forall \prof \in \allprofs \suchthat \MSP \nsubseteq \FBP$:
	\begin{enumerate}
		\item \label{it:minYUSumOLD} $\min \lprof(y) ≤ m - 1 - \max \lprof(y)$;
		\item \label{it:maxXUMaxCOLD} $\max \lprof(x) ≤ m - \max \lprof(y)$;
		\item \label{it:minXUOLD} $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y) + 1)$;
		\item \label{it:maxYUOLD} $\max \lprof(y) ≤ \frac{2 m - 2}{3}$;
		\item \label{it:maxXUMOLD} $\max \lprof(x) ≤ \floor{\frac{m - 1}{2}}$;
		\item \label{it:maxXLOLD} $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$;
		\item \label{it:minYLOLD} $\max \lprof(y) - \floor{\frac{m - 1}{2}} + 1 ≤ \min \lprof(y)$;
		\item \label{it:minYUMOLD} $\min \lprof(y) ≤ \floor{\frac{m - 1}{2}} - 1$;
		\item \label{it:maxXUMaxOLD} $\max \lprof(x) ≤ \max \lprof(y) - 1$;
		\item \label{it:maxXLMinOLD} $\min \lprof(y) + 1 ≤ \max \lprof(x)$;
		\item \label{it:minYUMaxOLD} $\min \lprof(y) ≤ \max \lprof(y) - 2$;
		\item \label{it:minYL2OLD} $2 ≤ \min \lprof(y)$;
		\item \label{it:maxYLOLD} $4 ≤ \max \lprof(y)$;
		\item \label{it:minYLCOLD} $2 \max \lprof(y) - m + 1 ≤ \min \lprof(y)$;
		\item \label{it:deltaOLD} $d(\lprof(x)) - d(\lprof(y)) ≤ \floor{\frac{m - 1}{2}} - 2$.
	\end{enumerate}
\end{theorem}
\begin{proof}
From \cref{th:rhoMinOLD} \cref{it:singVCOLD}, $\card{\argmax \lprof(x)} = \card{\argmax \lprof(y)} = 1$, thus we can define $\argmax \lprof(x) = \set{\ibar}$. Furthermore, $\argmax \lprof(x) \cap \argmax \lprof(y) = \emptyset$ as per \cref{th:rhoMinOLD} \cref{it:singVbisOLD}, thus, we can define $\argmax \lprof(y) = \set{i}$. 

Note that $\forall \prof \in \allprofs, z \in \POP: \sum \lprof(z) ≤ m - 1$.
In particular, $y \in PE$ requires $\sum \lprof(y) ≤ m - 1$, equivalently, \cref{it:minYUSumOLD}.

From \cref{th:rhoMinOLD} \cref{it:rhoMinOLD}, $\forall w \succ_i y: x \succeq_{\ibar} w$.
Also, by definition of $\lprof$, $\card{{\prefto_i}(y)} = \lprof(y)_i$.
We obtain $\lprof(x)_{\ibar} ≤ m - \lprof(y)_i$, or equivalently by definition of $i$ and $\ibar$, \cref{it:maxXUMaxCOLD}.

As $(d \circ \lprof)(y) < (d \circ \lprof)(x)$ (equivalently, $(d \circ \lprof)(y) + 1 ≤ (d \circ \lprof)(x)$), we obtain \cref{it:minXUOLD}.

From \cref{it:minXUOLD}, $\max \lprof(y) ≤ \max \lprof(x) - \min \lprof(x) + \min \lprof(y) - 1$, whence, using \cref{it:minYUSumOLD,it:maxXUMaxCOLD} and $- \min \lprof(x) ≤ 0$, $\max \lprof(y) ≤ m - \max \lprof(y) + m - 1 - \max \lprof(y) - 1$, equivalently, \cref{it:maxYUOLD}.

%Observe that $\exists z \in \allalts \suchthat \lprof(z)_i ≤ \khalf \land \lprof(z)_{\ibar} ≤ \khalf$. That’s because $\card \set{z \in \allalts \suchthat \lprof(z)_i ≤ \khalf} = \khalf + 1$ and there are only $\card \set{z \in \allalts \suchthat \lprof(z)_{\ibar} > \khalf} = m - (\khalf + 1) = \floor{\frac{m - 1}{2}} < \khalf + 1$ positions that do not satisfy $\lprof(z)_{\ibar} ≤ \khalf$.
%It follows that $\argmin \max \lprof ≤ \khalf$, which establishes \cref{it:maxXUMOLD}.
\Cref{it:maxXUMOLD} is established by \cref{th:equivOLD} \cref{it:rhoOLD}.

Combining \cref{it:minXUOLD} with $0 ≤ \min \lprof(x)$ establishes \cref{it:maxXLOLD}. 

Combining \cref{it:maxXUMOLD,it:maxXLOLD},
we get \cref{it:minYLOLD}.
%Using $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y)) - 1$, equivalently, $\min \lprof(x) + \max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$ together with $0 ≤ \min \lprof(x)$ yields $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x)$.

Combining \cref{it:minYLOLD} with $0 ≤ \max \lprof(y)$ establishes \cref{it:minYUMOLD}. 
%Also, $\min \lprof(y) < \max \lprof(x)$ by ordering, equivalently $\min \lprof(y) ≤ \max \lprof(x) - 1$, and $\max \lprof(x) ≤ \khalf$, thus $\min \lprof(y) ≤ \khalf - 1$.

By \cref{th:rhoMinOLD} \cref{it:orderOLD}, $\max \lprof(x) < \max \lprof(y)$, equivalently, \cref{it:maxXUMaxOLD}.

Similarly, by \cref{th:rhoMinOLD} \cref{it:orderOLD}, $\min \lprof(y) < \max \lprof(x)$, equivalently, \cref{it:maxXLMinOLD}.

Combining \cref{it:maxXUMaxOLD,it:maxXLMinOLD} yields \cref{it:minYUMaxOLD}.

From \cref{it:maxXLOLD,it:maxXUMaxOLD},
%Also, from $\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(x) ≤ \max \lprof(y) - 1$, thus 
$\max \lprof(y) - \min \lprof(y) + 1 ≤ \max \lprof(y) - 1$, whence \cref{it:minYL2OLD}.

Also, \cref{it:minYUMaxOLD,it:minYL2OLD} lead to \cref{it:maxYLOLD}.

\Cref{it:maxXUMaxCOLD,it:maxXLOLD} lead to \cref{it:minYLCOLD}.

Finally, from $\max \lprof(x) - \min \lprof(x) ≤ \max \lprof(x) ≤ \floor{\frac{m - 1}{2}}$ (\cref{it:maxXUMOLD}) and $- (\max \lprof(y) - \min \lprof(y)) ≤ -2$ (\cref{it:minYUMaxOLD}), we obtain \cref{it:deltaOLD}.
\end{proof}

\begin{corollary}
	\label{th:boundsSummaryOLD}
	$\forall \prof \in \allprofs \suchthat \MSP \nsubseteq \FBP$:
	\begin{enumerate}
		\item $4 ≤ \max \lprof(y) ≤ \frac{2 m - 2}{3}$;
		\item $\max \set{2, \max \lprof(y) - \khalf + 1, 2 \max \lprof(y) - m + 1} ≤ \min \lprof(y) ≤ \min \set{m - 1 - \max \lprof(y), \max \lprof(y) - 2, \khalf - 1}$;%
		\footnote{Seems like $\max \lprof(y) - \khalf + 1 < 2 \max \lprof(y) - m + 1$ so it has been omitted. 
		Indeed, $ 4 ≤ \frac{2m - 2}{3}$ thus $7 ≤ m$ thus $m - \khalf ≤ \frac{2m - 2}{3}$ thus $1 - \khalf ≤ 1 + \frac{2m - 2}{3} - m$, and then what?}
		\item $\max \set{\min \lprof(y) + 1, \max \lprof(y) - \min \lprof(y) + 1} ≤ \max \lprof(x) ≤ \min \set{\khalf, \max \lprof(y) - 1, m - \max \lprof(y)}$;
		\item $\min \lprof(x) ≤ \max \lprof(x) - (\max \lprof(y) - \min \lprof(y) + 1)$.
	\end{enumerate}
\end{corollary}

\section{Examples with m = 13}
Define $\epsilon = \max \lprof(y) - \max \lprof(x)$. We have $\epsilon ≤ \minineq[\POP] - 1$.

When $\rho = 6$, to ensure $\FBP = \set{x}$, must put $\set{a, b, c, d, e, f, g} \setminus \set{x}$ after $x$, hence, every alternative among $\set{h, i, j, k, l, m}$ must be better than $x$ for $2$, thus, $\argmin_{\POP} (d \circ \lprof) = h$, whatever $\minineq[\POP]$: any alternative among $\set{i, j, k, l, m}$ in between $h$ and $x$ for $2$ is Pareto-dominated by $h$ and any alternative among $\set{i, j, k, l, m}$ better than $h$ for $2$ has a greater spread.

\begin{example}
	$m = 13$, $\minineq[\FBP] = 6$, $\minineq[\POP] = 2$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$, with $g$ not just after $a$.
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 6$, $\minineq[\POP] = 3$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & h & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 6$, $\minineq[\POP] = 4$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & h & & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 6$, $\minineq[\POP] = 5$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & h & & & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 2$, $\rho = 6$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& \bm{b}	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{b}
		\end{array}
	\end{equation}
	Put $\set{a, c, d, e, f, g}$ after $b$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 2$, $\rho = 5$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & g & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 3$, $\rho = 6$, hence $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& \bm{b}	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & h & & \bm{b}
		\end{array}
	\end{equation}
	Put $\set{a, c, d, e, f, g}$ after $b$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 3$, $\rho = 5$, $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & g & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 3$, $\rho = 5$, $\epsilon = 2$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & h & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f, g}$ after $a$ (some constraints omitted).
\end{example}

\begin{example}
	$m = 13$, $\minineq[\FBP] = 4$, $\minineq[\POP] = 2$, $\rho = 6$, $\epsilon = 1$.
	\begin{equation}
		\begin{array}{lllllllllllll}
			a	& b	& \bm{c}	& d	& e	& f	& g	& h	& i & j & k & l & m\\
			& & & & & h & \bm{c}
		\end{array}
	\end{equation}
\end{example}

\section{Examples with m = 9 and m = 11}
For $m = 9$, some of the constraints are: $\minineq[\FBP] \in \intvl{3, 4}$, $\rho \in \intvl{3, 4}$ and $\minineq[\POP] \in \intvl{2, 3}$.

The following illustrates the general construction process. 
\begin{example}
	Example for $m = 9$, $\ineq(x) = \rho = 4$, $\minineq[\POP] = 3$.
	\begin{equation}
		\begin{array}{lllllllll}
			a	& b	& c	& d	& e	& f	& g	& h	& i\\
			\scriptscriptstyle{h} & \scriptscriptstyle{i} & f & \scriptscriptstyle{g} & a & \scriptscriptstyle{b} & \scriptscriptstyle{c} & \scriptscriptstyle{d} & \scriptscriptstyle{e}
		\end{array}
	\end{equation}

	To complete the preference of the second individual so that $\FBP = \set{a}$ and the Paretian minimizers of dispersion is $f$, just put $\set{b, c, d, e}$ worst than $a$ and $\set{g, h, i}$ in the remaining places, in any order.

	Note that putting $e$ just after $a$ might actually be significantly different than other permutations of the set $\set{b, c, d, e}$.
\end{example}

\begin{example}
	$m = 9$, $\minineq[\FBP] = 3$, $\rho = 3$, $\minineq[\POP] = 2$.
	\begin{equation}
		\begin{array}{lllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i\\
			& & e & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d}$ after $a$.
\end{example}

\begin{example}
	$m = 9$, $\minineq[\FBP] = 3$, $\rho = 4$, $\minineq[\POP] = 2$.
	\begin{equation}
		\begin{array}{lllllllll}
			a	& \bm{b}	& c	& d	& e	& f	& g	& h	& i\\
			& & & f & \bm{b}
		\end{array}
	\end{equation}
	Put $\set{a, c, d, e}$ after $b$.
\end{example}

\begin{example}
	$m = 9$, $\minineq[\FBP] = 4$ (hence $\rho = 4$), $\minineq[\POP] = 2$.
	\begin{equation}
		\begin{array}{lllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i\\
			& & & f & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e}$ after $a$.
\end{example}

\begin{example}
	$m = 9$, $\minineq[\FBP] = 4$ (hence $\rho = 4$), $\minineq[\POP] = 3$.
	\begin{equation}
		\begin{array}{lllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i\\
			& & f & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e}$ after $a$.
\end{example}

\begin{example}
	$m = 11$, $\minineq[\FBP] = 4$, $\rho = 4$, $\minineq[\POP] = 3$.
	\begin{equation}
		\begin{array}{lllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k\\
			& & & g & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f}$ after $a$.
\end{example}

\begin{example}
	$m = 11$, $\minineq[\FBP] = 4$, $\rho = 4$, $\minineq[\POP] = 3$, alternative.
	\begin{equation}
		\begin{array}{lllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k\\
			& & f & & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e}$ after $a$.
\end{example}

\begin{example}
	$m = 11$, $\minineq[\FBP] = 5$, $\minineq[\POP] = 2$.
	\begin{equation}
		\begin{array}{lllllllllll}
			\bm{a}	& b	& c	& d	& e	& f	& g	& h	& i & j & k\\
			& & & & g & \bm{a}
		\end{array}
	\end{equation}
	Put $\set{b, c, d, e, f}$ after $a$.
\end{example}

\section{Which \acp{SCR} are compromises?}
Let $\sigma: \alllosses → \R^+$ be an inequality measure, minimal exactly for constant loss vectors: $\forall l \in \alllosses: [\sigma(l) = 0] ⇔ [l_1 = l_2]$.
Let $\Sigma$ denote the set of functions satisfying this condition. 

Let $\argmin_{\POP} (\sigma \circ \lprof) = \set{x \in \POP \suchthat (\sigma \circ \lprof)(x) = \min_{y \in \POP} (\sigma \circ \lprof)(y)}$ denote the least unequal alternatives among the Pareto-optimal ones, according to the measure $\sigma \circ \lprof$.
Given a SCR $f$, say that $f$ is Pareto Compromise Compatible (PCC) iff $\exists \sigma \in \Sigma \suchthat \forall \prof \in \allprofs: f(\prof) \cap \argmin_{\POP} (\sigma \circ \lprof) ≠ \emptyset$.

We consider in particular the inequality measure $d \in \Sigma$ defined as the absolute difference between the losses. 

Below: copied from our other paper.

\label{sec:more2voters}
In this section we assume $n\geq 3$ and leave the analysis of $n=2$ to the
next section.

\subsection{BK-compromises}
\label{sec:BKn3}
Given any $k\in \intvl{1, m}$, we write $n_{k}(x,P)=\#\{i\in
N\mid r_{\prefi}(x)\leq k\}$ for the \emph{$k$-support} that $x$ gets at $P$, that is, the number of individuals for whom the rank of alternative $x\in A$ is lower than or equal to $k$ in the profile $P\in $ $L(A)^{N}$.
Note that $n_{k}(x,P)\in \intvl{1, n}$ is non-decreasing on $k$ and $n_{m}(x,P)=n.$ For each $q\in \intvl{1,n}$, we define $\rho_{q}(x,P)=\min \{k\in \intvl{1,m} \suchthat n_{k}(x,P)\geq q\}$ as the minimal rank $k$ at which the $k$-support that $x$ gets at $P$ is at least $q$. We
write $\rho _{q}(P) = \min_{x \in A} \set{\rho_{q}(x, P)}$ for the minimal rank $k$ at which the $k$-support that some alternative gets at $P$ is at least $q$. \textit{A Brams and Kilgour (BK) compromise with threshold }$q$ is the
\ac{SCR} $f_{q}$ defined for each $P\in \linors^N$ as $f_{q}(P)=\{x\in A | n_{\rho _{q}(P)}(x,P)\geq n_{\rho _{q}(P)}(y,P)$ $\forall y\in A\}.$

\begin{theorem}
	\label{th:FBsatsPC}
Let $n\geq 3$ and $m\geq 3.$ The BK compromise $f_{n}$ satisfies PC.
\end{theorem}

\begin{proof}
Define $\bar{\sigma } \in \Sigma$ as, $\forall l \in \intvl{0,m-1}^N$: $\bar\sigma(l) = 1$ iff $\exists i, j \in N \suchthat l_i ≠ l_j$; $\bar\sigma(l) = 0$ otherwise.
Considering any $x \in f_n(P)$, let us show that $x \in \mustar[\bar{\sigma}]$. Because $x \in f_n(P)$, $x \in \paretopt(P)$, and therefore, suffices to show that $\forall y \in \paretopt(P)$, $\bar{\sigma}(\lambda_P(y)) ≥ \bar{\sigma}(\lambda_P(x))$. Given the choice of $\bar{\sigma}$, picking any $y \in \paretopt(P)$ with $y≠x$, suffices to show that $\bar{\sigma}(\lambda_P(y)) = 1$, equivalently, that $\exists i, j \in N \suchthat r_{\prefi}(y) ≠ r_{\pref_j}(y)$. 
Because $x \in f_n(P)$, $\rho_n(P) = \rho_n(x, P) = \max_{i \in N} r_{\prefi}(x)$.
It follows from $\rho_n(P) = \min_{z \in A} \set{\rho_n(z, P)}$ that $\rho_n(y, P) ≥ \rho_n(x, P)$, thus, $\exists i \in N \suchthat r_{\prefi}(y) ≥ \rho_n(P)$. 
Also, $y \in \paretopt(P)$ implies that $\exists j \in N \suchthat r_{\pref_j}(y) < r_{\pref_j}(x)$, thus $\exists j \in N \suchthat r_{\pref_j}(y) < \rho_n(P)$. 
Therefore, $r_{\prefi}(y) ≠ r_{\pref_j}(y)$.
\end{proof}

\section{Two voters case}
Copied from our submitted paper.

In \cref{sec:more2voters} we focused on the analysis of voting rules when the number of voters involved into the decision process is greater than two. Keeping the notation introduced in \cref{sec:notation}, we consider here the case $n=2$. Two individuals express their preference over a set of alternatives $A$, and the goal is to find a common agreement on the alternative to select. This class of problems is often referred to as bargaining problems. In addition to \textit{fallback bargaining (FB)} \citep{Brams2001} (defined in \cref{sec:BKn3}) we consider three prominent solutions of the literature.

\textit{Pareto-and-Veto rules (PV)} \citep{Laslier2020} distribute a veto power of $v_1$ and $v_2$ alternatives to voters 1 and 2, respectively, with $v_1+v_2=m-1$. So, every voter $i=1,2$ (simultaneously) vetoes his worst $v_i$ alternatives. The \ac{SCR} picks all non-vetoed and Pareto optimal alternatives.

The \textit{Veto-Rank mechanism (VR)} is commonly used in the selection of arbitrators \citep{Clippel2014}. Given a list of $m$ (odd) alternatives (that are candidates to be arbitrators), each of the two voters (that are the two parties that must agree on an arbitrator) simultaneously vetoes his worst $\frac{m-1}{2}$ alternatives. The selected alternatives are the ones with the highest Borda score among the non-vetoed alternatives.

Again within the context of selecting arbitrators, \citet{Clippel2014} propose and analyze \textit{Shortlisting (SL)} where one of the two parties starts by vetoing her worst $\frac{m-1}{2}$ alternatives ($m$ being odd), and then the second party chooses her best alternative out of the remaining ones. As the outcome of the procedure depends on the party that starts, symmetry among players is ensured by defining the solution as the union of the two outcomes where one and the other party starts.

\begin{definition}
	Given any $m \geq 7$, a spread measure $\sigma \in \Sigma$ satisfies condition $D_m$ iff 
	$\sigma(\ceil{\frac{m}{2}}, \ceil{\frac{m}{2}} - 2) < \sigma(0, \ceil{\frac{m}{2}} - 1)$ and 
	$\sigma(\ceil{\frac{m}{2}} - 2, \ceil{\frac{m}{2}}) < \sigma(\ceil{\frac{m}{2}} - 1, 0)$.
\end{definition}

For $m=7$ the condition requires $\sigma(4, 2) < \sigma(0, 3)$ and $\sigma(2, 4) < \sigma(3, 0)$ which is reasonable in our context. When the value of $m$ is larger, the condition appears even more convincing. As $m$ grows, the distance between $0$ and $\ceil{\frac{m}{2}} - 1$ grows, while the distance between $\ceil{\frac{m}{2}}$ and $\ceil{\frac{m}{2}} - 2$ remains constant. Requiring, for example, the spread of $(15, 13)$ to be smaller than the spread of $(0, 14)$ is very reasonable.

We write $\Sigma^{D_{m}} \subseteq \Sigma$ for the set of spread measures that satisfy condition $D_{m}$. 

\begin{theorem} \label{th:2votPCC}
	Let $m \geq 7$. Under $\Sigma^{D_{m}}$, FB and PV fail PCC. Furthermore, when $m$ is odd, VR and SL also fail PCC.
\end{theorem}
\begin{proof}
	Take any $m \geq 7$ and any $\sigma \in \Sigma^{D_m}$. Define $\alpha = \ceil{\frac{m}{2}} - 1$ and $\beta = \ceil{\frac{m}{2}} - 2$. It follows from $\sigma \in \Sigma^{D_{m}}$, that $\sigma(\alpha + 1, \beta) < \sigma(0, \beta + 1)$ and $\sigma(\beta, \alpha + 1) < \sigma(\beta + 1, 0)$.
	For $m$ odd, note that $\alpha + \beta + 2 = m$ and consider the profile $P$ where voter $i_1$ has the preference $x \succ a_1 \succ … \succ a_\alpha \succ y \succ b_1 \succ … \succ b_\beta$ and voter $i_2$ has the preference $b_1 \succ … \succ b_\beta \succ y \succ x \succ a_1 \succ … \succ a_\alpha$. For $m$ even, note that $\alpha + \beta + 3= m$, and define the profile $P$ in the same way, except that a supplementary alternative $z$ is added at the bottom of both rankings.
	
	Note that $\sigma(\lambda_{P}(y)) = \sigma(\alpha + 1, \beta)$ and that $\sigma(\lambda_{P}(x)) = \sigma(0, \beta + 1)$. 
	Therefore, $\sigma(\lambda_{P}(y)) < \sigma(\lambda_{P}(x))$. As $y$ is not Pareto-dominated, an \ac{SCR} that uniquely picks $x$ at $P$ cannot be PCC. In a similar vein, at the profile $P'$ which is obtained by the inversion of the preferences of $i_1$ and $i_2$ at $P$, an \ac{SCR} that is PCC cannot pick $x$ uniquely.	
	
	The proof will be concluded by showing that FB, PV, and (when $m$ is odd) VR and SL all pick only $x$ at $P$ or at $P'$.
	
	We readily see that FB picks only $x$ at $P$ (and at $P'$) since $x$ is the first alternative which reaches the unanimous consent.
	For PV, let $v_{i_1} ≥ v_{i_2}$ (thus $v_{i_1} ≥ \ceil{\frac{m-1}{2}} ≥ \ceil{\frac{m-2}{2}} = \beta + 1$ and $v_{i_2} ≤ \floor{\frac{m - 1}{2}} = \ceil{\frac{m - 2}{2}} = \alpha$), and consider the profile $P$. Observe that the first voter vetoes at least $y$ and every $b_j$ ($1 ≤ j ≤ \beta$) while no voter vetoes $x$. As $x$ Pareto-dominates every $a_j$ ($1 ≤ j ≤ \alpha$), PV picks only $x$ at $P$. When $v_{i_2} ≥ v_{i_1}$, a similar reasoning yields that PV picks only $x$ at $P'$.
	
	Now let $m$ be odd.
	
	For VR, a reasoning similar to the one applied to PV yields $x$ as the unique choice at $P$: each voter vetoes her worst $\frac{m-1}{2}$ alternatives, thus $i_1$ vetoes $y$ and every $b_j$ ($1 ≤ j ≤ \beta$) and $i_2$ vetoes every $a_j$ ($1 ≤ j ≤ \alpha$). The alternative $x$ is the only non-vetoed alternative, so it is selected as the sole winner.
	
	Finally, SL also picks $x$, as it is the unique winner no matter which voter starts the veto phase. If $i_1$ starts, $y$ and every $b_j$ ($1 ≤ j ≤ \beta$) get vetoed, then $i_2$ chooses her best alternative out of the remaining ones which is $x$. If $i_2$ starts, every $a_j$ ($1 ≤ j ≤ \alpha$) get vetoed, then $i_1$ chooses her best alternative which is $x$. 
\end{proof}
\end{document}
